---
title: 'Probability of Arrival Pathways: Mental Models'
author: "Annabelle"
date: "2025-02-12"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
## Apparently this includes more checks.. 
library("VGAM")
library(patchwork)
```
*Currently assuming that we are generating arrivals over 25 years, not 50 years* 

## Wild deer movement from disease front (Wild deer other states --> wild deer VT)
Measure distance from VT border to place where prevalence is at least .5% (disease front)
We expect that distance to decrease over time
*Note - this doesn't ever seed an infection in Vermont directly because it never crosses the border in our time horizon* 
```{r, echo=FALSE, fig.align = 'center'}
### Starting distance - where is .5% disease front
PA_counties_data <- readxl::read_excel("Spread_Diffusion/Data/PACountyPrev_9_8_24.xlsx", col_names = TRUE) # assembled from PA heat map - 7/8/24

head(PA_counties_data)

## Based on the detected prevalence in PA, only two counties are above 5% 
# Fulton is closer (~360 miles)

starting_distance <- 360 # should be y-intercept 

# 360 = b*3^(-.05x+20)
b = 1.03247e-07
x = seq(from = 0, to = 25, by = 1) # years 
y = b*3^(-.05*x+20) # this is the relationship I expect to see (right shifted negative exponential, not sure what slope should be)

df <- as.data.frame(cbind(x, y))

ggplot(data = df) +
  geom_line(aes(x = x, y = y, color = "dist")) + 
  scale_color_manual(
    values = c("dist" = "darkred")) +
  labs(y = "Distance from VT border", x = "Time (Years)")

```
*Not sure what the slope would be here..* 



## Contaminated Hunting Gear (Wild deer other states --> wild deer VT)

* Nothing formalized in mechanistic breakdown 

Proposed: 

* The number of hunters hunting in CWD positive areas will increase over time 
* The probability that this will result in prions brought back to Vermont, binding to the soil, and infecting deer stays the same 
* But prions can infect multiple deer (so Poisson distribution) 
* We are not accounting for accumulation and decay of prions 
* The following would be run each year 

```{r, fig.align = 'center', echo=FALSE}
### Based on TN data, proportion is 0.0552 of hunters hunting out of state

b = 1.03247e-07
x = seq(from = 0, to = 25, by = 1) # years 
y = b*3^(.05*x+20) # this is the relationship I expect to see (right shifted negative exponential, not sure what slope should be)

df <- as.data.frame(cbind(x, y))

ggplot(data = df) +
  geom_line(aes(x = x, y = y, color = "dist")) + 
  scale_color_manual(
    values = c("dist" = "darkgreen")) +
  labs(y = "No Hunters hunting in CWD positive areas", x = "Time (Years)", 
       title="The no. hunters hunting in CWD+ areas \nincreases over time")
```

The intercept and slope are likely wrong here, but I want to set up the mechanisms first 


We then use a Poisson distribution to estimate how many hunters are coming back to Vermont,
the prions the bring with them are binding to the soil, and those prions are infecting wild deer.

Using the number of hunters hunting in CWD+ areas each year, we can find the number of infected deer created in Vermont two ways (the following are set around year 10 (n = 600)), either
a) set up a Poisson distribution with a tiny lambda (.001)
```{r, fig.align = 'center', echo=FALSE}
n = 600
lambda = .01
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom contaminated hunting gear (rpois)")
```

or
b) create a 0-inflated Poisson using a binomial that then calls a Poisson distribution if we have a 1

```{r, fig.align = 'center', echo=FALSE}
## Manual option 
# ifelse(rbinom(n, size = 1, prob = p) > 0, 0, rpois(n, lambda = lambda))

## Apparently this includes more checks.. 
library("VGAM")

n = 600 
lambda = .01
p = .0013
hist(rzipois(n, lambda = lambda, pstr0 = p), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom contaminated hunting gear (rzipois)")
```

Pretty similar result so question: Is there value in setting an additional parameter p? (Second approach)


```{r, eval = FALSE, echo=FALSE, include = FALSE}
### ### ### ### ### ### ### ### ### ### ### ### ### ### Old approach 

#https://insects.shinyapps.io/Probability_Dists/

int = -7.2
slope = .09

X = 40

predicted_prob = plogis(int + X*slope)
byhand = 1/ (1 + exp(-(int+X*slope)))

int = -7
slope = 1.9

X = seq(0, .40, by = 0.01)
predicted_prob = plogis(int + X*slope)
# plot(X, predicted_prob)

df <- as.data.frame(cbind(X, predicted_prob))

ggplot(data = df) +
  geom_line(aes(x = X, y = predicted_prob, color = "ppe")) + 
  scale_color_manual(
    values = c("ppe" = "blue")) +
  labs(y = "Annual Probability of the arrival of a single infected deer", x = "Prevalence")
# 
# What should n be here? 
# p is pulled from graph above.. could just assume .0013

## Manual option 
ifelse(rbinom(n, size = 1, prob = p) > 0, 0, rpois(n, lambda = lambda))

## Apparently this includes more checks.. 
library("VGAM")

n = 100 
lambda = 1
p = .0013
hist(rzipois(n, lambda = lambda, pstr0 = p))
```




## Animal movement (Wild deer other states --> wild deer VT)

*Nothing formalized in mechanistic breakdown*

Proposed: 

* As soon as the disease is a certain distance from Vermont (Less than 40 miles?)
* There is a chance that animals/scavengers can move prions/pieces of carcasses over the Vermont border 
* So draw from the following (Poisson) probability distribution every year the disease front is a certain distance away 

```{r, fig.align = 'center', echo=FALSE}
n = 10
lambda = .1
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom animal movement (rpois)")
```

Question - what should n and lambda be?




```{r, echo=FALSE, include = FALSE, fig.align = 'center'}

### ### ### ### ### ### ### ### ### ### ### ### ### ### Old approach 

x1 = seq(0, .40, by = 0.01)
beta0 = -5.95 
beta1 = 6 
beta2 = 1 

# Lets say it needs to be at least 40 miles from boarder first, after that, need to normalize from 40 to 0 miles so that have 40 miles = 0 and 0 miles from boarder = 1 
miles = seq(0, 40, by = 1)

normalize <- function(x, na.rm = TRUE) {
    return((x- max(x)) /(min(x)-max(x)))
}

miles_norm <- normalize(miles)
x2 = .5 ## Basically going to adjust the slope based on how far away the disease is
mu = (beta0) + (beta1 + beta2*x2)*x1 
p <- plogis(mu) # need logistic tranformation function (do by hand)

# plot(x1, p)

df <- as.data.frame(cbind(x1, p))

ggplot(data = df) +
  geom_line(aes(x = x1, y = p, color = "animal_move")) + 
  scale_color_manual(
    values = c("animal_move" = "purple")) +
  labs(y = "Probability", x = "Prevalence")

```






## Carcass movement (Wild deer other states --> wild deer VT)

**Mechanistic breakdown (parameterized with lit review)**

* No. of Hunters
* Proportion of hunters hunting in state with CWD
* prob of harvesting at least one deer
* proportion of hunters bringing high risk parts back
* prob( that a deer has CWD | harvested )
* proportion of deer going to processor
* probability of disposing of parts on the landscape
* number of deer interacting with carcass
* number of days carcass is on landscape
* prob( infection | exposed to CWD + carcass)



Lots of actions: 

* A	Ban high risk parts from CWD positive states // movement of parts (status quo) 
* C	Ban moose parts imports (change language to cervids) // movement of parts 
* F	Enhanced guidelines for taxidermists/processors // movement of prions in state 
* H	Private landowner carcass disposal guidelines // compliance + movement of parts 
* I	Incorporate CWD info during license buying process // compliance 
* J	Ban high risk parts from out of state for all states regardless of CWD status // movement of parts 
* L	Ban taxidermists/processors from accepting/handling any parts from outside of Vermont // movement of parts 


Proposal: 

1.  Number of hunters hunting in CWD+ areas is a function of time
2.  Probability of harvesting a deer is a function of actions (compliance)
3.  Lambda increases over time (is this linear?) (proxy for prevalence increasing)
4.  This results in a zero-inflated poisson with n = number of hunters, probability = compliance, lambda = prevalence

Q - how do we include movement of parts actions? Change lambda? 
Q - Ignore distinction between private landowner disposal and processor/taxidermist disposal? 


```{r, eval=FALSE, include=FALSE}

### Draw of the number of deer harvested in a CWD area (function of time and prevalence)
  # Linked to natural movement model 

### Probability of hunter moving parts back (status quo value is a draw from 12%) - change with actions 

# Split into taxidermist + processors (55%) // private landowners (45%)



x1 = seq(0, .40, by = 0.01)
beta0 = -2
beta1 = 6 
beta2 = 1 
beta4 = 2 

# Lets say it needs to be at least 40 miles from boarder first, after that, need to normalize from 40 to 0 miles so that have 40 miles = 0 and 0 miles from boarder = 1 
miles = seq(0, 40, by = 1)

normalize <- function(x, na.rm = TRUE) {
    return((x- max(x)) /(min(x)-max(x)))
}

miles_norm <- normalize(miles)
x2 = 1 ## Basically going to adjust the slope based on how far away the disease is
mu = (beta0) + (beta1 + beta2*x2)*x1 
p <- plogis(mu) # need logistic tranformation function (do by hand)

plot(x1, p)

```






## Urine lures (captive other states --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**
* No. of Hunters
* Percent of hunters using natural lures
* Total number of lures used per year
* Probability of a natural lure having CWD / volume of urine put down? (.00003) 
* prob infection

Not including accumulation

Two actions:

* Ban natural scent-based lures
* Ban all scent-based lures (including synthetic)

```{r, eval = FALSE, echo=FALSE, include = FALSE, fig.align = 'center'}

### ### ### ### ### ### ### ### ### ### ### ### ### ### Old approach 

int = -7
slope = .17
beta1 = -.07 #for action 1
beta2 = -.14 # for action 2

X = seq(0, 25, by = 1) # time (25 years)

x1 = action1 = 0 # ban natural scent-based lures
x2 = action2 = 0 # ban all lures 

prob_noaction = plogis(int + X*(slope + beta1*x1 + beta2*x2))

# If only ban scent-based 
x1 = actionB = 1 # ban natural scent-based lures
x2 = actionK = 0 # ban all lures 

prob_nonaturalscents = plogis(int + X*(slope + beta1*x1 + beta2*x2))

# If ban all 

x1 = action1 = 0 # ban natural scent-based lures
x2 = action2 = 1 # ban all lures 

prob_ban_all = plogis(int + X*(slope + beta1*x1 + beta2*x2))
# plot(X, predicted_prob)

df <- as.data.frame(cbind(X, prob_noaction, prob_nonaturalscents, prob_ban_all))
## This is off... 
ggplot(data = df) +
  geom_line(aes(x = X, y = prob_noaction, color = "prob_noaction")) + 
  geom_line(aes(x = X, y = prob_nonaturalscents, color = "prob_nonaturalscents")) + 
  geom_line(aes(x = X, y = prob_ban_all, color = "prob_ban_all")) + 
  scale_color_manual(
    values = c("prob_noaction" = "purple", "prob_nonaturalscents" = "blue", "prob_ban_all" = "black" ),
    labels = c("Ban all scent-based lures (including synthetic)", "no actions","Ban natural scent lures (Status Quo)")  # Manual labels for the legend
  )+
  labs(color = "Legend", y = "Probability", x = "Time (years)")
```

3 different probability distributions 
I set these up by establishing the mean and variance for each action and then fitting those to a beta distribution 
The histograms show the probability of seeding the infection of a single deer each year from 1000 simulations

```{r, warning=FALSE, echo=FALSE, message=FALSE}
est_beta_params <- function(mu, var) {
  # check that the var <mu(1-mu), if greater, use the largest possible
  if(var > mu*(1-mu)){var = mu*(1-mu)-.00001}
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}


prob_noaction_mu = .02
prob_nonaturalscents_mu = .007
prob_ban_all_mu = .0025

prob_noaction_var = .005
prob_nonaturalscents_var = .0025
prob_ban_all_var = .0005

### Make baby data table 

means <- c(prob_noaction_mu, prob_nonaturalscents_mu, prob_ban_all_mu)
vars <- c(prob_noaction_var, prob_nonaturalscents_var, prob_ban_all_var)

showdf <- as.data.frame(rbind(means, vars))
colnames(showdf) <- c("No Action", "No Natural Scents (Status Quo)", "Ban All")

showdf


b_params_noact <- est_beta_params(prob_noaction_mu, prob_noaction_var)
b_params_nonaturalscents <- est_beta_params(prob_nonaturalscents_mu, prob_nonaturalscents_var)
b_params_ban_all <- est_beta_params(prob_ban_all_mu, prob_ban_all_var)

noaction_sim <- rbeta(1000, b_params_noact$alpha, b_params_noact$beta)
nonaturalscents_sim <- rbeta(1000, b_params_nonaturalscents$alpha, b_params_nonaturalscents$beta)
ban_all_sim <- rbeta(1000, b_params_ban_all$alpha, b_params_ban_all$beta)

prob_sims_df <- cbind(noaction_sim, nonaturalscents_sim, ban_all_sim)

# ggplot(data = prob_sims_df) +
#   geom_histogram(aes(x = noaction_sim, fill = "prob_noaction")) + 
#   geom_histogram(aes(x = nonaturalscents_sim, fill = "prob_nonaturalscents")) + 
#   geom_histogram(aes(x = ban_all_sim, fill = "prob_ban_all")) + 
#   scale_color_manual(
#     values = c("prob_noaction" = "purple", "prob_nonaturalscents" = "blue", "prob_ban_all" = "grey" ),
#     labels = c("Ban all scent-based lures (including synthetic)", "no actions","Ban natural scent lures (Status Quo)")  # Manual labels for the legend
#   )+
#   labs(color = "Legend", y = "Probability", x = "Time (years)")

p_noact <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = noaction_sim)) + 
  labs(x = "Annual probability of seeding the infection of a single deer", title = "No Actions") +
  ylim(0,1000) +
  coord_cartesian(xlim = c(NA, .1))
p_natural <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = nonaturalscents_sim)) + 
  labs( x = "Annual probability of seeding the infection of a single deer", title = "No Natural Scents \n (Status Quo)") +
  ylim(0,1000) +
  coord_cartesian(xlim = c(NA, .1))
p_banall <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = ban_all_sim)) + 
  labs(x = "Annual probability of seeding the infection of a single deer", title = "Ban All") +
  coord_cartesian(xlim = c(NA, .1))


(p_noact + p_natural + p_banall) +
plot_layout(axis_titles = "collect")

```

So how many hunters are using lures in the state? (this is n (per year?))

Two options:

* Instead of having different ns for each action, lets assume that the level of us is included in the probability 
* n would be different for each action, no?
  * No action = number hunters using lures
  * ban natural lures = number hunters using lures
  * ban all lures = number of bad actors using natural

Currently using The proportion of hunters using natural lures (.05) * no. Vermont Hunters (63600) for n

Also not sure what we put for lambda here... (.01?)
Just using the average (mu) for each action, not sure if that's right 

```{r, echo=FALSE}
# proportion of hunters hunting out state
prop_use_natural_lures <- .05 
noVThunters <- 63600

prob_noaction_mu = .02
prob_nonaturalscents_mu = .007
prob_ban_all_mu = .0025

n = prop_use_natural_lures* noVThunters
lambda = .01

hist(rzipois(n, lambda = lambda, pstr0 = prob_noaction_mu), xlab = "Count of infected deer", main = "No Action")
hist(rzipois(n, lambda = lambda, pstr0 = prob_nonaturalscents_mu), xlab = "Count of infected deer", main = "No Natural Scents \n (Status Quo)")
hist(rzipois(n, lambda = lambda, pstr0 = prob_ban_all_mu), xlab = "Count of infected deer", main = "Ban All")

# main = "Count of infected deer per year \nfrom animal movement (rpois)"
# These plots all look the same
```



## Fenceline interactions (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**

* Number of captive cervid facilities
* prob( a captive cervid is infected | exposure) 
* total number of captive deer
* prob of direct contact [.2628]
* prob ( infection | contact ) [.333]

Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  For each positive DETECTED at a captive cervid farm (this is run in parallel with the population model), 
2.  Run a zero-inflated Poisson distribution using probability from lit review and set rate (n = average number of deer? - this would probably overestimate --> set to 10 )

unsure what to put for lambda here(.1)? 

```{r, echo=FALSE}
prob <- .2628 * .333
lambda = .1
n = 10 

hist(rzipois(n, lambda = lambda, pstr0 = prob), xlab = "Count of infected deer", main = "Status Quo")

hist(rzipois(n, lambda = lambda, pstr0 = prob*.5), xlab = "Count of infected deer", main = "Double fencing")

```

If facilities are closed, this would just be 0. 






## Breakouts (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)** 
Given you are able to recover the deer:

* number of proximity events over the coarse of a days escape
* Probability of deer making direct contact given they are in the same area
* number of days a deer escapes given it is recovered
* number of days in a year
* prob ( infection | contact ) 

Given you are not able to recover the deer:

* number of proximity events over the coarse of a days escape
* Probability of deer making direct contact given they are in the same area
* number of days in a year
* prob ( infection | contact ) 

Are we accounting for indirect contact here?


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  Run a Poisson distribution using probability from lit review (n = average number of deer? - this would probably overestimate --> set to 10 )



## Environemental contamination (Captive deer VT --> wild deer VT)


**Nothing formalized in mechanistic breakdown**


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  Run a Poisson distribution using probability from lit review (n = average number of deer? - this would probably overestimate --> set to 10 )



## Carcass disposal of captives (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**

* prob( at least 1 captive cervid is infected | exposure) 
* total number of captive deer
* proportion of captive deer in facility butchered / year
* probability of disposing of parts on the landscape
* number of deer interacting with carcass
* number of days carcass is on landscape
* prob( infection | exposed to CWD + carcass)


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  All captive cervids are tested post-mortum, correct? So this wouldn't be a pathways?






