---
title: 'Probability of Arrival Pathways: Mental Models'
author: "Annabelle"
date: "2025-02-12"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
## Apparently this includes more checks.. 
library("VGAM")
library(patchwork)
```
*Currently assuming that we are generating arrivals over 25 years, not 50 years* 

## Wild deer movement from disease front (Wild deer other states --> wild deer VT)

* Nothing formalized in mechanistic breakdown 

Proposed: 

* Poisson arrival distribution  
* Distance of front is a predictor, as is natal dispersal 

Measure distance from VT border to place where prevalence is at least .5% (disease front)
We expect that distance to decrease over time; Do we expect it to reach Vermont?
```{r, echo=FALSE, fig.align = 'center'}
### Starting distance - where is .5% disease front
PA_counties_data <- readxl::read_excel("Spread_Diffusion/Data/PACountyPrev_9_8_24.xlsx", col_names = TRUE) # assembled from PA heat map - 7/8/24

# head(PA_counties_data)

## Based on the detected prevalence in PA, only two counties are above 5% 
# Fulton is closer (~360 miles)

starting_distance <- 360 # should be y-intercept 

# 360 = b*3^(-.05x+20)
b = 1.03247e-07
x = seq(from = 0, to = 25, by = 1) # years 
y = b*3^(-.05*x+20) # this is the relationship I expect to see (right shifted negative exponential, not sure what slope should be)

df <- as.data.frame(cbind(x, y))

ggplot(data = df) +
  geom_line(aes(x = x, y = y, color = "dist")) + 
  scale_color_manual(
    values = c("dist" = "darkred")) +
  labs(y = "Distance from VT border", x = "Time (Years)")

```

*Not sure what the slope would be here..*


```{r, echo=FALSE}
## Source : https://www.jstor.org/stable/pdf/1382386.pdf
## Might be newer data but didn't see it here - https://academic.oup.com/jmammal/article-pdf/86/3/623/7026399/86-3-623.pdf

distanceskm <- c(4,8,12,16,20,24,28,32,36,40,56)
femalecount <- c(28,0,0,0,1,1,0,0,2,0,3)
malecount <- c(17,8,9,2,1,0,1,0,3,2,1)

distancemiles <- 0.621371 * distanceskm

dispersal_1993 <- data.frame(distancemiles, femalecount, malecount)

# Change from count to % 
dispersal_1993$femalepercent <- femalecount / (sum(femalecount))
dispersal_1993$malepercent <- malecount / (sum(malecount))

```

```{r, echo=FALSE}
int = 3 
slope1 = -.09 # because smaller distance increases likelihood

distfromVT = seq(0, 360, by = 1)
predicted_prob = plogis(int + slope1*distfromVT)

plot(distfromVT, predicted_prob, main = "Probability of a single infection walking \nto Vermont", 
     xlab = "Distance from Vermont", ylab = "Probability")


## Now include natal dispersal 
slope2 = .05 # positive because larger distance increases likelihood

natal = seq(0, 40, by = 5)

## Will have to draw natal disperstion for each individual?? 

predicted_prob = plogis(int + (slope1*distfromVT + slope2*40) )
plot(distfromVT, predicted_prob, main = "Probability of a single infection walking \nto Vermontnset natal dispersal (40 mi)", 
     xlab = "Distance from Vermont", ylab = "Probability")
```

"plogis(int + (slope1*distfromVT + slope2*40)"


so now what do we set n as?
lambda is pulled from above probability depending on distance and random draw of natal dist
do we pull random distribution of natal for each individual?

```{r, echo=FALSE}
n = 600
lambda = .01
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom contaminated hunting gear (rpois)")
```




## Contaminated Hunting Gear (Wild deer other states --> wild deer VT)

* Nothing formalized in mechanistic breakdown 

Proposed: 

* The number of hunters hunting in CWD positive areas will increase over time 
* The probability that this will result in prions brought back to Vermont, binding to the soil, and infecting deer stays the same 
* But prions can infect multiple deer (so Poisson distribution) 
* We are not accounting for accumulation and decay of prions 
* The following would be run each year 

```{r, fig.align = 'center', echo=FALSE}
### Based on TN data, proportion is 0.0552 of hunters hunting out of state

b = 1.03247e-07
x = seq(from = 0, to = 25, by = 1) # years 
y = b*3^(.05*x+20) # this is the relationship I expect to see (right shifted negative exponential, not sure what slope should be)

df <- as.data.frame(cbind(x, y))

ggplot(data = df) +
  geom_line(aes(x = x, y = y, color = "dist")) + 
  scale_color_manual(
    values = c("dist" = "darkgreen")) +
  labs(y = "No Hunters hunting in CWD positive areas", x = "Time (Years)", 
       title="The no. hunters hunting in CWD+ areas \nincreases over time")
```


We then use a Poisson distribution to estimate how many hunters are coming back to Vermont,
the prions the bring with them are binding to the soil, and those prions are infecting wild deer.

Using the number of hunters hunting in CWD+ areas each year, we can find the number of infected deer created in Vermont two ways (the following are set around year 10 (n = 600)), either
a) set up a Poisson distribution with a tiny lambda (.001)
```{r, fig.align = 'center', echo=FALSE}
n = 600
lambda = .01
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom contaminated hunting gear (rpois)")
```



```{r, eval = FALSE, echo=FALSE, include = FALSE}
### ### ### ### ### ### ### ### ### ### ### ### ### ### Old approach 

#https://insects.shinyapps.io/Probability_Dists/

int = -7.2
slope = .09

X = 40

predicted_prob = plogis(int + X*slope)
byhand = 1/ (1 + exp(-(int+X*slope)))

int = -7
slope = 1.9

X = seq(0, .40, by = 0.01)
predicted_prob = plogis(int + X*slope)
# plot(X, predicted_prob)

df <- as.data.frame(cbind(X, predicted_prob))

ggplot(data = df) +
  geom_line(aes(x = X, y = predicted_prob, color = "ppe")) + 
  scale_color_manual(
    values = c("ppe" = "blue")) +
  labs(y = "Annual Probability of the arrival of a single infected deer", x = "Prevalence")
# 
# What should n be here? 
# p is pulled from graph above.. could just assume .0013

## Manual option 
ifelse(rbinom(n, size = 1, prob = p) > 0, 0, rpois(n, lambda = lambda))

## Apparently this includes more checks.. 
library("VGAM")

n = 100 
lambda = 1
p = .0013
hist(rzipois(n, lambda = lambda, pstr0 = p))
```




## Animal movement (Wild deer other states --> wild deer VT)

*Nothing formalized in mechanistic breakdown*

Proposed: 

* Likelihood of animals/scavengers can move prions/pieces of carcasses over the Vermont border is a function of how far away the disease is 
* So draw from the following (Poisson) probability distribution every year based on distance of disease front 

```{r}
int = 1 
slope1 = -.09 # because smaller distance increases likelihood

distfromVT = seq(0, 360, by = 1)
predicted_prob = plogis(int + slope1*distfromVT)


plot(distfromVT, predicted_prob, main = "Probability of a single infection \nfrom scavenger movement", 
     xlab = "Distance from Vermont", ylab = "Probability")
```

Do we need to modify lambda or just pull resulting probability from graph above? 
lambda = n*p.... 
Need to clarify how this translates to parameters in r function...
```{r, fig.align = 'center', echo=FALSE}
n = 10
lambda = .6
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom animal movement (rpois)")
```

Question - what should n and lambda be?



## Carcass movement (Wild deer other states --> wild deer VT)

**Mechanistic breakdown (parameterized with lit review)**

* No. of Hunters
* Proportion of hunters hunting in state with CWD
* prob of harvesting at least one deer
* proportion of hunters bringing high risk parts back
* prob( that a deer has CWD | harvested )
* proportion of deer going to processor
* probability of disposing of parts on the landscape
* number of deer interacting with carcass
* number of days carcass is on landscape
* prob( infection | exposed to CWD + carcass)



Lots of actions: 

* A	Ban high risk parts from CWD positive states // movement of parts (status quo) 
* C	Ban moose parts imports (change language to cervids) // movement of parts 
* F	Enhanced guidelines for taxidermists/processors // movement of prions in state 
* H	Private landowner carcass disposal guidelines // compliance + movement of parts 
* I	Incorporate CWD info during license buying process // compliance 
* J	Ban high risk parts from out of state for all states regardless of CWD status // movement of parts 
* L	Ban taxidermists/processors from accepting/handling any parts from outside of Vermont // movement of parts 


Proposal: 

1.  Number of hunters hunting in CWD+ areas is a function of time (this is n)
2.  Lambda increases over time - function of compliance, distance of disease, and likelihood of parts moving 

Q - Ignore distinction between private landowner disposal and processor/taxidermist disposal? I have these as same effect size in the model

For each of the actions, I have a relationship set up, but I'm not sure if we want to see each of these individually
The gist is that the slope of the probability is modified by actions labeled compliance, and slop is modified by both the distance of the disease and the movement of parts (more movement increases probability)
There is one action that changes slope and intercept because I think that would impact compliance and number of parts that would be moved. 

Q - What combinations do we want to see here? 
```{r, echo = FALSE, include=FALSE}

### ### ### Set up Null model 

### intercept 
# modified by compliance
### Slope
# modified by prevalence distance
# modified by movement of parts 

int = 1 
slope1 = -.01 # because smaller distance increases likelihood

compliance <- -1 # large negative number reduces probability 
likelihoodpartsmove <- -9 # large negative number reduces probability 

distfromVT = seq(0, 360, by = 1)
predicted_prob = plogis((int + compliance) + (slope1*distfromVT + likelihoodpartsmove))

plot(distfromVT, predicted_prob)

### ### ### Set up how strong leavers should be 

### ### Include Action A 
### A	Ban high risk parts from CWD positive states // movement of parts (status quo) 

compliance <- 0 # turn off
ActionA <- 1
betaA <- -.5

predicted_prob = plogis((int + compliance) + (slope1*distfromVT + ActionA*betaA))

plot(distfromVT, predicted_prob)



### ### Include Action C
### C	Ban moose parts imports (change language to cervids) // movement of parts  

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 1
betaC <- -.05

predicted_prob = plogis((int + compliance) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC))

plot(distfromVT, predicted_prob)



### ### Include Action F
### F	Enhanced guidelines for taxidermists/processors // movement of prions in state   

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 0
ActionF <- 1
betaF <- -2

predicted_prob = plogis((int + compliance) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC + ActionF*betaF))

plot(distfromVT, predicted_prob)


### ### Include Action H
### H	Private landowner carcass disposal guidelines // compliance + movement of parts  

# Assuming this will be same order of magnitude as tax/processor 
# but also adding changes to the intercept for compliance

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 0
ActionF <- 0
ActionH1 <- 1
betaH1 <- -2
ActionH2 <- 1
betaH2 <- -.5

predicted_prob = plogis((int + ActionH2*betaH2) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC + ActionF*betaF + ActionH1*betaH1))

plot(distfromVT, predicted_prob)


### ### Include Action I
### I	Incorporate CWD info during license buying process // compliance 

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 0
ActionF <- 0
ActionH1 <- 0
ActionH2 <- 0
ActionI <- 1
betaI <- -4

predicted_prob = plogis((int + ActionH2*betaH2 + ActionI*betaI) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC + ActionF*betaF + ActionH1*betaH1))

plot(distfromVT, predicted_prob)




### ### Include Action J
### J	Ban high risk parts from out of state for all states regardless of CWD status // movement of parts

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 0
ActionF <- 0
ActionH1 <- 0
ActionH2 <- 0
ActionI <- 0
ActionJ <- 1
betaJ <- -4


predicted_prob = plogis((int + ActionH2*betaH2 + ActionI*betaI) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC + ActionF*betaF + ActionH1*betaH1 + ActionJ*betaJ))

plot(distfromVT, predicted_prob)



### ### Include Action L
### L	Ban taxidermists/processors from accepting/handling any parts from outside of Vermont // movement of parts 

compliance <- 0 # turn off
ActionA <- 0
ActionC <- 0
ActionF <- 0
ActionH1 <- 0
ActionH2 <- 0
ActionI <- 0
ActionJ <- 0
ActionL <- 1
betaL <- -4


predicted_prob = plogis((int + ActionH2*betaH2 + ActionI*betaI) + (slope1*distfromVT + ActionA*betaA + ActionC*betaC + ActionF*betaF + ActionH1*betaH1 + ActionJ*betaJ + ActionL*betaL))

plot(distfromVT, predicted_prob)

### Not sure which combinations to show... 

# df <- as.data.frame(cbind(x1, p))
# 
# ggplot(data = df) +
#   geom_line(aes(x = x1, y = p, color = "animal_move")) + 
#   scale_color_manual(
#     values = c("animal_move" = "purple")) +
#   labs(y = "Probability", x = "Prevalence")
```


n would be based on the following.. 
```{r, fig.align = 'center', echo=FALSE}
### Based on TN data, proportion is 0.0552 of hunters hunting out of state

b = 1.03247e-07
x = seq(from = 0, to = 25, by = 1) # years 
y = b*3^(.05*x+20) # this is the relationship I expect to see (right shifted negative exponential, not sure what slope should be)

df <- as.data.frame(cbind(x, y))

ggplot(data = df) +
  geom_line(aes(x = x, y = y, color = "dist")) + 
  scale_color_manual(
    values = c("dist" = "darkgreen")) +
  labs(y = "No Hunters hunting in CWD positive areas", x = "Time (Years)", 
       title="The no. hunters hunting in CWD+ areas \nincreases over time")
```

Draw n depending on the time step


Do we need to modify lambda or just pull resulting probability from graph above? 
lambda = n*p.... 
Need to clarify how this translates to parameters in r function...
```{r, fig.align = 'center', echo=FALSE}
n = 10
lambda = .6
hist(rpois(n, lambda = lambda), xlab = "Count of infected deer", main = "Count of infected deer per year \nfrom animal movement (rpois)")
```








## Urine lures (captive other states --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**
* No. of Hunters
* Percent of hunters using natural lures
* Total number of lures used per year
* Probability of a natural lure having CWD / volume of urine put down? (.00003) 
* prob infection

Not including accumulation

Two actions:

* Ban natural scent-based lures
* Ban all scent-based lures (including synthetic)


3 different probability distributions 
I set these up by establishing the mean and variance for each action and then fitting those to a beta distribution 
The histograms show the probability of seeding the infection of a single deer each year from 1000 simulations

```{r, warning=FALSE, echo=FALSE, message=FALSE}
est_beta_params <- function(mu, var) {
  # check that the var <mu(1-mu), if greater, use the largest possible
  if(var > mu*(1-mu)){var = mu*(1-mu)-.00001}
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}


prob_noaction_mu = .02
prob_nonaturalscents_mu = .007
prob_ban_all_mu = .0025

prob_noaction_var = .005
prob_nonaturalscents_var = .0025
prob_ban_all_var = .0005

### Make baby data table 

means <- c(prob_noaction_mu, prob_nonaturalscents_mu, prob_ban_all_mu)
vars <- c(prob_noaction_var, prob_nonaturalscents_var, prob_ban_all_var)

showdf <- as.data.frame(rbind(means, vars))
colnames(showdf) <- c("No Action", "No Natural Scents (Status Quo)", "Ban All")

showdf


b_params_noact <- est_beta_params(prob_noaction_mu, prob_noaction_var)
b_params_nonaturalscents <- est_beta_params(prob_nonaturalscents_mu, prob_nonaturalscents_var)
b_params_ban_all <- est_beta_params(prob_ban_all_mu, prob_ban_all_var)

noaction_sim <- rbeta(1000, b_params_noact$alpha, b_params_noact$beta)
nonaturalscents_sim <- rbeta(1000, b_params_nonaturalscents$alpha, b_params_nonaturalscents$beta)
ban_all_sim <- rbeta(1000, b_params_ban_all$alpha, b_params_ban_all$beta)

prob_sims_df <- cbind(noaction_sim, nonaturalscents_sim, ban_all_sim)

# ggplot(data = prob_sims_df) +
#   geom_histogram(aes(x = noaction_sim, fill = "prob_noaction")) + 
#   geom_histogram(aes(x = nonaturalscents_sim, fill = "prob_nonaturalscents")) + 
#   geom_histogram(aes(x = ban_all_sim, fill = "prob_ban_all")) + 
#   scale_color_manual(
#     values = c("prob_noaction" = "purple", "prob_nonaturalscents" = "blue", "prob_ban_all" = "grey" ),
#     labels = c("Ban all scent-based lures (including synthetic)", "no actions","Ban natural scent lures (Status Quo)")  # Manual labels for the legend
#   )+
#   labs(color = "Legend", y = "Probability", x = "Time (years)")

p_noact <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = noaction_sim)) + 
  labs(x = "Annual probability of seeding the infection of a single deer", title = "No Actions") +
  ylim(0,1000) +
  coord_cartesian(xlim = c(NA, .1))
p_natural <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = nonaturalscents_sim)) + 
  labs( x = "Annual probability of seeding the infection of a single deer", title = "No Natural Scents \n (Status Quo)") +
  ylim(0,1000) +
  coord_cartesian(xlim = c(NA, .1))
p_banall <- ggplot(data = prob_sims_df) +
  geom_histogram(aes(x = ban_all_sim)) + 
  labs(x = "Annual probability of seeding the infection of a single deer", title = "Ban All") +
  coord_cartesian(xlim = c(NA, .1))


(p_noact + p_natural + p_banall) +
plot_layout(axis_titles = "collect")

```

So how many hunters are using lures in the state? (this is n (per year?))

Two options:

* Instead of having different ns for each action, lets assume that the level of us is included in the probability 
* n would be different for each action, no?
  * No action = number hunters using lures
  * ban natural lures = number hunters using lures
  * ban all lures = number of bad actors using natural

Currently using The proportion of hunters using natural lures (.05) * no. Vermont Hunters (63600) for n

Also not sure what we put for lambda here... (.01?)
Just using the average (mu) for each action, not sure if that's right 

```{r, echo=FALSE}
# proportion of hunters hunting out state
prop_use_natural_lures <- .05 
noVThunters <- 63600

prob_noaction_mu = .02
prob_nonaturalscents_mu = .007
prob_ban_all_mu = .0025

n = prop_use_natural_lures* noVThunters
lambda = .01

hist(rzipois(n, lambda = lambda, pstr0 = prob_noaction_mu), xlab = "Count of infected deer", main = "No Action")
hist(rzipois(n, lambda = lambda, pstr0 = prob_nonaturalscents_mu), xlab = "Count of infected deer", main = "No Natural Scents \n (Status Quo)")
hist(rzipois(n, lambda = lambda, pstr0 = prob_ban_all_mu), xlab = "Count of infected deer", main = "Ban All")

# main = "Count of infected deer per year \nfrom animal movement (rpois)"
# These plots all look the same
```



## Fenceline interactions (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**

* Number of captive cervid facilities
* prob( a captive cervid is infected | exposure) 
* total number of captive deer
* prob of direct contact [.2628]
* prob ( infection | contact ) [.333]

Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  For each positive DETECTED at a captive cervid farm (this is run in parallel with the population model), 
2.  Run a zero-inflated Poisson distribution using probability from lit review and set rate (n = average number of deer? - this would probably overestimate --> set to 10 )

unsure what to put for lambda here(.1)? 

```{r, echo=FALSE}
prob <- .2628 * .333
lambda = .1
n = 10 

hist(rzipois(n, lambda = lambda, pstr0 = prob), xlab = "Count of infected deer", main = "Status Quo")

hist(rzipois(n, lambda = lambda, pstr0 = prob*.5), xlab = "Count of infected deer", main = "Double fencing")

```

If facilities are closed, this would just be 0. 






## Breakouts (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)** 
Given you are able to recover the deer:

* number of proximity events over the coarse of a days escape
* Probability of deer making direct contact given they are in the same area
* number of days a deer escapes given it is recovered
* number of days in a year
* prob ( infection | contact ) 

Given you are not able to recover the deer:

* number of proximity events over the coarse of a days escape
* Probability of deer making direct contact given they are in the same area
* number of days in a year
* prob ( infection | contact ) 

Are we accounting for indirect contact here?


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  Run a Poisson distribution using probability from lit review (n = average number of deer? - this would probably overestimate --> set to 10 )



## Environemental contamination (Captive deer VT --> wild deer VT)


**Nothing formalized in mechanistic breakdown**


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  Run a Poisson distribution using probability from lit review (n = average number of deer? - this would probably overestimate --> set to 10 )



## Carcass disposal of captives (Captive deer VT --> wild deer VT)


**Mechanistic breakdown (parameterized with lit review)**

* prob( at least 1 captive cervid is infected | exposure) 
* total number of captive deer
* proportion of captive deer in facility butchered / year
* probability of disposing of parts on the landscape
* number of deer interacting with carcass
* number of days carcass is on landscape
* prob( infection | exposed to CWD + carcass)


Actions: 

* A	Double fencing  (results in probability being halved? )
* B Close captive facilities 

Proposal: 

1.  All captive cervids are tested post-mortum, correct? So this wouldn't be a pathways?






