---
title: "Surveillance Handout Workshop"
output: word_document
date: "2024-1-24"
---

Outstanding Issues:
* How to address cost information (only inlcude MI?)
* Need to make theme/look of handout consistent 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, include=FALSE}
### ### Load libraries 
library(tidyverse)
library(readxl)
library(knitcitations)
library(kableExtra) ## devtools::install_github("kupietz/kableExtra") #some issue needed patching
library(flextable) #kable doesn't knit to word
library(directlabels) # To add labels to lines in ggplot

### ### Read in data
countytbl <- read_excel("Tablesfrom2022DeerHarvestReport.xlsx", sheet = "Table012")
PercentSeason <- read_excel("Tablesfrom2022DeerHarvestReport.xlsx", sheet = "PercentSeason")

### ### Initial cleaning
# Drop extra columns from dataframe 
countytbl <- countytbl %>% dplyr::select(-Total, -HarvestperSqMile)
countytbl_long <- countytbl %>% 
  pivot_longer(cols = !c(County, Town), names_to = "Season", values_to = "Count", values_drop_na = T)

# join percents to main df by Season
fulldf <- countytbl_long %>% full_join(PercentSeason, by = "Season")

## Assume have 1/3 of total from riffle season 
fulldf <- fulldf %>% 
  mutate(Count = case_when(Season == "Regular" ~ Count*.1, Season != "Regular" ~ Count))

set.seed(123)
fulldf <- fulldf %>%
  add_column(AdultBuckCount = NA, AdultDoeCount = NA, MaleFawnCount = NA, FemaleFawnCount = NA)
for(i in 1:nrow(fulldf)){
  fulldf[i, 9:12] <- t(rmultinom(1, as.numeric(fulldf[i,4]) , prob = fulldf[i,5:8]))
}
```

### The relationship between prevalence, confidence, and number of samples


The graph below shows the number of samples required to have a 90%, 95%, or 99% confidence (see colored lines) in detecting *at least one* case of chronic wasting disease, under various assumed prevalences (x-axis) **for ANY spatial unit of interest**. Prevalence refers to the proportion of the population that is diseased. Under a simplified random sample (SRS), the confidence level heavily influences the number of samples needed and associated costs. 


```{r genDFs, include= FALSE}
## From this, create 2 different data sets: (aggregated at county level but could do other boundaries)
# 1) All harvested indiviudals
# 2) All sampled inidividuals (just youth and open riffle (which is regular here??))


## Cost points for each sample
# low - Indiana - 16/sample
# High own lab - MI - 189/sample
# High no lab - Ohio - 200/sample

Indiv_county_ALL <- fulldf %>% 
  group_by(County) %>% 
  summarise(AdultBuckCount = sum(AdultBuckCount), 
            AdultDoeCount = sum(AdultDoeCount),
            MaleFawnCount = sum(MaleFawnCount),
            FemaleFawnCount = sum(FemaleFawnCount)) %>% 
  rowwise() %>%
  mutate(ContyTotal = sum(AdultBuckCount, AdultDoeCount, MaleFawnCount, FemaleFawnCount)) %>% 
  mutate(Indiana = 16) %>% 
  mutate(Michigan = 189) %>% 
  mutate(Ohio = 200)

Indiv_county_CheckStations <- fulldf %>% 
  filter(Season == "Youth" | Season == "Regular") %>% 
  group_by(County) %>% 
  summarise(AdultBuckCount = sum(AdultBuckCount), 
            AdultDoeCount = sum(AdultDoeCount),
            MaleFawnCount = sum(MaleFawnCount),
            FemaleFawnCount = sum(FemaleFawnCount)) %>% 
  rowwise() %>%
  mutate(ContyTotal = sum(AdultBuckCount, AdultDoeCount, MaleFawnCount, FemaleFawnCount)) %>% 
  mutate(Indiana = 16) %>% 
  mutate(Michigan = 189) %>% 
  mutate(Ohio = 200)
```

<br>
```{r statewide table, echo=FALSE}
State_ALL <- sum(Indiv_county_ALL$ContyTotal)
State_CheckStations <- sum(Indiv_county_CheckStations$ContyTotal)

SRSno.sampleCalcfunc <- function(prevalence = .01, confidence = .99){
  log(-(confidence - 1))/(log(1 - prevalence))
}

### Create vectors of alpha and prevalence 
#vecalpha <- c(seq(.01, .1, by = .001)) # Change this to select 4 values of alpha that we care about
vecalpha <- c(.01, .05, .1, .2) #99, 95, 90, 80
#vecprev <- c(.001, .01, .1)
vecprev <- c(seq(.01, .1, by = .0001))

All_NoSampSRS <- data.frame()
setcounter <- 1
for(i in vecalpha){
  for(j in vecprev){
    HoldNo <- SRSno.sampleCalcfunc(prevalence = j, confidence = 1 - i)
    IDCharString <- paste0("Alpha_", i, "_", "Prevalence_", j)
    ## Create counter that depends on i & j
    setcounter
    All_NoSampSRS[setcounter, 1] <- IDCharString
    All_NoSampSRS[setcounter, 2] <- HoldNo
    setcounter <- setcounter + 1
  }
}

colnames(All_NoSampSRS) <- c("Surveillance Design", "No. Samples Needed")
All_NoSampSRS$'No. Samples from Check Stations' <- rep(State_CheckStations, nrow(All_NoSampSRS))
All_NoSampSRS$'No. Samples from All Harvest' <- rep(State_ALL, nrow(All_NoSampSRS))
```

```{r, fig.cap="Figure 1. No. Samples Needed under Different Surveillance Designs. The color of each line corresponds to the confidnece level.", echo = F, message=FALSE, fig.width=10, fig.height=7}
All_NoSampSRS_grph_setup <- All_NoSampSRS %>%
  separate_wider_delim(cols = `Surveillance Design`, delim = "_", names = c("alpha_label", "Alpha", "prev_label", "Prevalence")) %>% 
  mutate(Confidence = 1- as.numeric(Alpha)) # Create Confidence
All_NoSampSRS_grph_setup$Prevalence <- as.numeric(All_NoSampSRS_grph_setup$Prevalence)

#ggplot(All_NoSampSRS_grph_setup) + 
#  geom_point(aes(x = Prevalence, y = `No. Samples Needed`, color = Alpha))



ggplot(All_NoSampSRS_grph_setup) + 
  geom_point(aes(x = Prevalence, y = `No. Samples Needed`, color = as.factor(Confidence) ) ) +
  scale_y_continuous(breaks=seq(0, 500,20), limits = c(0, 500) 
  ) + 
  #scale_x_continuous(breaks=seq(0, 1, .01)) +
  labs(color = "Confidence") + 
  theme(axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=16,colour="black"),
        legend.text=element_text(size=12), 
        panel.background = element_rect(fill = "white", colour = "grey50"))
```

<br>
<br>


### Estimating our power to detect CWD across counties using all available samples

We use values from the Vermont 2022 Deer Harvest report to estimate counts of individuals in strata (adult male, adult female, yearling male, and yearling female), harvested in Vermont’s 14 counties, across harvest seasons (archery, youth, novice, October muzzle, regular, and December muzzle). We use an multinomial with probability informed by percentage breakdowns in the deer harvest report to estimate the count of each strata in a county by season. Vermont only collects samples from check stations from the first weekend of the regular season and from the youth hunt. We estimate that checked individuals from the regular season were only 10% of the total harvest. Our dataset only includes individuals harvested in the youth hunt and 10% of individuals harvested in the regular season. 
<br>

With these data, we calculate the number of samples needed to detect CWD at a given prevalence and statistical assurance (alpha). Alpha is the confidence that population-level CWD prevalence is at or below the threshold level. 


For each county, we can take the prevalence where we would have the power to detect CWD at least once for a given confidence. 


```{r County2, fig.cap="Figure 2. Prevalence Level from Available Samples per County. Each color corresponds to a different confidence level", echo=FALSE}
Prev_Indiv_county_CheckStations <- Indiv_county_CheckStations %>% 
  mutate(Alpha_01 = .01) %>% 
  mutate(Alpha_05 = .05) %>% 
  mutate(Alpha_1 = .1) %>% 
  pivot_longer(cols = c("Alpha_01", "Alpha_05", "Alpha_1"), 
               names_to = "Alpha", values_to = "Alpha_level") %>% 
  ### Now calc prev from number of samples 
  # extra step to make sure not too wonky 
  mutate(confidencecalc = 1 - Alpha_level) %>% 
  mutate(EstPrev = 1 - (Alpha_level)^(1/ContyTotal) )

### How are prevalence values still so high? 

## Set up table
Prev_Indiv_county_CheckStations_tbl <- Prev_Indiv_county_CheckStations %>% 
  select(County, ContyTotal, confidencecalc, EstPrev )

#colnames(Prev_Indiv_county_CheckStations_tbl) <- c("County", "No. Samples", "Confidence Level", "Prevalence")

#kable(Prev_Indiv_county_CheckStations_tbl,
#      caption = "Table 9. Total Prevalence that for a Set Level of Alpha Given the Total Number of Samples #in a County for the Check Stations Dataset",
#      align = "lrrr") %>% 
#  kable_styling(bootstrap_options = "striped")

# The palette with grey:
cbPalette <- c("#999999", "#56B4E9", "#009E73")


ggplot(Prev_Indiv_county_CheckStations_tbl) + 
  geom_point(aes(x = EstPrev, y = factor(County), color = factor(confidencecalc))) + 
  labs(x = "County Level Prevalence", y = "County", color = "Confidence Level") + 
  scale_color_brewer(palette = "Dark2")

```


<br>


### For a given state wide prevalence level, what is the achieved county-level prevalence given all estimated checked animals?

Here, we divide the total number of samples needed for specific combinations of state-level confidence and prevalence proportionally by WMU and then identify whether the number of samples available at a WMU level through biological check stations is enough to meet the proportional allocation. The proportional number of samples needed per WMU is based on the proportion of the total harvest generated by that WMU. 


```{r CountyPlot, fig.cap="Figure 3. Resulting Prevalence at County Level. Each unique combination of color and line type corresponds to one of the 14 counties in Vermont. The proportion of harvest per county is given by the number on each line.", fig.width=10, fig.height=11, echo=FALSE, message = F, warning = F}
SRS_for_dfs_func <- function(Indiv_county_ALL){

  Indiv_county_ALL_SRS <- Indiv_county_ALL %>% 
      #Figure out proportional harvest per country 
  mutate(prop = ContyTotal/(sum(Indiv_county_ALL$ContyTotal)))
    
  ### Create vectors of alpha and prevalence 
vecalpha <- c(.01, .05, .1, .2) #99, 95, 90, 80
vecprev <- c(seq(.01, .1, by = .0001))

## Do alpha 
Acolfunc <- function(df, n){
      varname <- paste0("alpha.", n)
      df %>%
         mutate(!!varname := 1 * n) ### Fining a way to add row of the same value 
}
Indiv_county_ALL_alph <- Indiv_county_ALL_SRS
for(i in vecalpha){
    Indiv_county_ALL_alph <- Acolfunc(df = Indiv_county_ALL_alph, n = i)
}
Indiv_county_ALL_alph <- Indiv_county_ALL_alph %>% pivot_longer(cols = starts_with("alpha"),
             names_to = "Alpha", values_to = "Alpha_level")
             

## Set up prev 
Prevcolfunc <- function(df, n){
      varname <- paste0("Prevalence", n)
      df %>%
         mutate(!!varname := 1 * n)
}
Indiv_county_ALL_Prev <- Indiv_county_ALL_SRS
for(i in vecprev){
    Indiv_county_ALL_Prev <- Prevcolfunc(df = Indiv_county_ALL_Prev, n = i)
}
Indiv_county_ALL_Prev <- Indiv_county_ALL_Prev %>% pivot_longer(cols = starts_with("Prevalence"),
             names_to = "Prevalence", values_to = "Prevalence_level")

LongAlph_Prev <- Indiv_county_ALL_Prev %>% full_join(Indiv_county_ALL_alph, 
  by = c("County","AdultBuckCount","AdultDoeCount","MaleFawnCount","FemaleFawnCount",
         "ContyTotal","Indiana","Michigan","Ohio", "prop"))


Indiv_county_ALL_SRS <- LongAlph_Prev %>% 
  ### Now calc number of samples needed 
  mutate(NoSamples = log(-((1-Alpha_level) - 1))/(log(1 - Prevalence_level))) %>% 
  mutate(NoSamplesperCounty = NoSamples*prop) %>% #mult by proportion of harvest
  ## Now calculate costs
  mutate(Cost_Indiana = NoSamplesperCounty *Indiana) %>% 
  mutate(Cost_Michigan = NoSamplesperCounty *Michigan) %>% 
  mutate(Cost_Ohio = NoSamplesperCounty *Ohio) %>% 
  ## Do we have enough samples in the county (Y/N)
  mutate(TargetMeet = if_else((NoSamplesperCounty - ContyTotal)  > 0, "False", "True"))
}

Indiv_county_CheckStations_SRS <- SRS_for_dfs_func(Indiv_county_CheckStations)

#ggplot(Indiv_county_CheckStations_SRS) + 
#  geom_point(aes(x = Prevalence_level, y = NoSamplesperCounty, color = TargetMeet))+
#  facet_wrap(~County) + 
#   labs(x = "Prevalence", y = "No. Samples per County") 

## Old graph to see if could meet target, not informative when it's all true... 

Indiv_county_CheckStations_SRS <- Indiv_county_CheckStations_SRS %>% 
  mutate(county_prev = 1- (Alpha_level^(1/NoSamplesperCounty))) %>% 
  mutate(Confidence_num = (1 - Alpha_level) *100) %>%  #create confidence label
  mutate(Confidence = paste0(Confidence_num, "%", " confidence")) %>% 
  mutate(line_names = as.character(round(prop,2)))

# ggplot(Indiv_county_CheckStations_SRS) + 
#   geom_point(aes(x = Prevalence_level, y = county_prev, color = County))+
#  # facet_wrap(~Confidence) + 
#    labs(x = "State Wide Prevelance", y = "County Level Prevelence Achieved") + 
#   scale_y_continuous(expand=c(0, .105))+
#   geom_dl(aes(x = Prevalence_level, y = county_prev,label = line_names), method = list("last.points", cex=.8, hjust=1.2) ) +
#   labs(caption = "Note: The proportion of harvest per county is given in the text") 

Line_Options <- c(1,2,3,4,5,6)
col_vibrant <- c("#0077BB","#009988",
                 "#EE7733","#EE3377",  "#BBBBBB")

set.seed(123)
ggplot(Indiv_county_CheckStations_SRS) + 
  geom_line(aes(x = Prevalence_level, y = county_prev, color = County, linetype = County), size = 1.25)+
 # facet_wrap(~Confidence) + 
   labs(x = "State Wide Prevelance", y = "County Level Prevelence Achieved") + 
  scale_y_continuous(expand=c(0, .105))+
  geom_dl(aes(x = Prevalence_level, y = county_prev,label = line_names), method = list("last.points", cex=.8, hjust=1.2) ) +
#  labs(caption = "Note: The proportion of harvest per county is given in the text")+ 
 scale_colour_manual(values = sample(col_vibrant, 14, replace = TRUE)) +
  scale_linetype_manual(values = sample(Line_Options, 14, replace = TRUE))

```

The smaller the proportion of harvest is for a county, the less power that county has to detect CWD and higher the resulting county-level prevalence will be for a given state prevalence level.



### Costs

Costs of surveillance vary with the scale of the surveillance program, whether hunters or others (e.g., VFWD staff, processors) are collecting the samples, and where the laboratory analyses are completed. Estimates of cost per sample range from $10/sample (current Vermont costs for low sample sizes) to $188/sample (estimate from Michigan which has a large, staff-based surveillance program).

### Prevalence at the state level

```{r, fig.cap="Figure 4. No. Samples Needed under Different Surveillance Designs. The color of each line corresponds to the confidnece level. Adult Buck Count totals 2688 and is not included on the graph.", echo = F, message=FALSE, fig.width=10, fig.height=7}
All_NoSampSRS_grph_setup <- All_NoSampSRS %>%
  separate_wider_delim(cols = `Surveillance Design`, delim = "_", names = c("alpha_label", "Alpha", "prev_label", "Prevalence")) %>% 
  mutate(Confidence = 1- as.numeric(Alpha)) # Create Confidence
All_NoSampSRS_grph_setup$Prevalence <- as.numeric(All_NoSampSRS_grph_setup$Prevalence)

#ggplot(All_NoSampSRS_grph_setup) + 
#  geom_point(aes(x = Prevalence, y = `No. Samples Needed`, color = Alpha))


## add horizontal line for avg number of checked deer per strata 
ABC <- sum(Indiv_county_CheckStations$AdultBuckCount)
ADC <- sum(Indiv_county_CheckStations$AdultDoeCount)
MFC <- sum(Indiv_county_CheckStations$MaleFawnCount)
FFC <- sum(Indiv_county_CheckStations$FemaleFawnCount)

#create data frame that contains horizontal line location
cutoff <- data.frame(yintercept=ADC, Lines='Adult Doe Count')
cutoff2 <- data.frame(yintercept=MFC, Lines='Male Fawn Count')
cutoff3 <- data.frame(yintercept=FFC, Lines='Female Fawn Count')


ggplot(All_NoSampSRS_grph_setup) + 
  geom_point(aes(x = Prevalence, y = `No. Samples Needed`, color = as.factor(Confidence) ) ) +
  scale_y_continuous(breaks=seq(0, 500,20), limits = c(0, 500) ,
    sec.axis = sec_axis(~ . * 189, name = "Cost (Michigan - 189$/sample)\n") #\n adds line break or space
  ) + 
  #scale_x_continuous(breaks=seq(0, 1, .01)) +
  labs(color = "Confidence") + 
  geom_hline(aes(yintercept=yintercept, linetype=Lines), cutoff, color = "blue") +
  geom_hline(aes(yintercept=yintercept, linetype=Lines), cutoff2, color = "darkgreen") +
  geom_hline(aes(yintercept=yintercept, linetype=Lines), cutoff3, color = "darkblue") + 
#  labs(caption = "Note: Adult Buck Count totals 2688 and is not included on the graph") + 
  theme(axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=16,colour="black"),
        legend.text=element_text(size=12), 
        panel.background = element_rect(fill = "white", colour = "grey50"))
```
