---
title: "LogitCheck"
output:
  pdf_document: default
  html_document: default
date: "2024-05-09"
---

Load in file and libraries 
```{r, message = FALSE, warning=FALSE}
source("CWD_model_Cross/functions/est_beta_params.R")
source("CWD_model_Cross/functions/allocate_deaths.R")
source("CWD_model_Cross/functions/MyFunctions.R")
source("CWD_model_Cross/cwd_stoch_model_cal_act.r")
source("CWD_model_Cross/ArrivalVectors.R")
source("CWD_model_Cross/functions/cwd_stoch_wrapper_mod.r")
source("CWD_model_Cross/functions/ComHypowSelectH.R") # 2 different functions for setting parameters
source("CWD_model_Cross/functions/ComHypowWeights_even.R") # 2 different functions for setting parameters
source("CWD_model_Cross/functions/Plot_funcs.R") # Basic Plots
source("CWD_model_Cross/functions/CompareAltsFuncwSetH_Plot_func.R") # use for multi strat single H
source("CWD_model_Cross/functions/CompareAltsFunc_Plot_func.R") # use for multi strat across multi H
library(foreach)
library(doParallel)
library(tidyverse)
library(reshape2)
library(patchwork)
```

```{r, message = FALSE, warning=FALSE}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.0,  beta.m = 0.0,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0,0,0,0,0), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 460
)

simsout_H1_w <- cwd_stoch_wrapper_setARV(params, nsims = 20, n.years = 25)

prev_wAct <- plot_stoch_prev_single(simsout_H1_w$counts, all.lines = TRUE)
 H1_abund <- plot_stoch_abundance(simsout_H1_w, all.lines = TRUE, error.bars)
# H1_harv <- plot_stoch_harvest(simsout_H1_w, harvesttype= 2)
 ### Not working!! ^^^

```




### Try turning on hunting actions on one by one

- not going to see impact of sharpshooting in hunting graphs because not collected as hunting
  just removed from larger population
- Also density dependent so action will only occur in until reach a power number 
* When change parameters in model to more extreme values, see this is working
*changed 300 removed to 1000, and changed stopping criteria from 1/3 to 1/6 of starting popn
* Lines 890 - 900 in model script 
```{r sharpshooting, message = FALSE, warning=FALSE, fig.cap= "Figure 1: Test sharpshooting action"}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(0,0,0,200,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0,1,0,0,0), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 1,
             nosampled = 460
)

simsout_H1_w <- cwd_stoch_wrapper_setARV(params, nsims = 20, n.years = 25)

prev_wAct <- plot_stoch_prev_single(simsout_H1_w$counts, all.lines = TRUE)
infect_w <- plot_stoch_infected_indiv(simsout_H1_w, all.lines = TRUE, error.bars)
# H1_harv <- plot_stoch_harvest(simsout_H1_w, all.lines, error.bars, detectbar, harvesttype= 1)

#plot_stoch_harvest(simsout_H1_w, all.lines, error.bars, detectbar, harvesttype= 2)
#plot_stoch_harvest(simsout_H1_w, all.lines, error.bars, detectbar, harvesttype= 3)

params$Action_sharpshooting <- 0

simsout_H1_wo <- cwd_stoch_wrapper_setARV(params, nsims = 20, n.years = 25)

infect_wo <- plot_stoch_infected_indiv(simsout_H1_wo, all.lines = TRUE, error.bars)

prev_woAct <- plot_stoch_prev_single(simsout_H1_wo$counts, all.lines = TRUE)

prev_wAct + prev_woAct

sharpshooteffect <- infect_w + infect_wo

ggsave(plot = sharpshooteffect, "CWD_model_Cross/MayWorkshopPlots/sharpshootplot.png",
       width = 6, height = 4)

## plot sharpshooting

  data <- simsout_H1_w$sharpshooting %>%
    filter(month %% 12 == 7) %>%
    filter(population > 0) %>% 
    group_by(sim, year) %>%
    dplyr::summarize(n = sum(population)) %>%
    arrange(sim, year)
  
sharpshoot <- ggplot(data = data, aes(x = year, y = n, group = sim)) +
    geom_line(color = "grey")

  
```




Action_lib_harvest
- Pulls an extra proportional amount of harvest (note this is pretty stochastic)

```{r lib harvest, message = FALSE, warning=FALSE, fig.cap= "Figure 3: Test 'libharvest' action (with action is on left)"}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(0,0,0,0,0,0,200,0,0,0,0,0,0,0,0,0,0,0,0,0, 0,1,0,0,0), 
             Action_young_bucks = 0, Action_lib_harvest = 1, Action_sharpshooting = 0,
             nosampled = 460
)

simsout_w_act <- cwd_stoch_wrapper_setARV(params, nsims = 50, n.years = 25)
allharv_w <- plot_stoch_harvest(simsout_w_act, harvesttype= 1)


antlerless_w <- plot_stoch_harvest(simsout_w_act,  harvesttype= 3)


params$Action_lib_harvest <- 0

simsout_wo_act <- cwd_stoch_wrapper_setARV(params, nsims = 50, n.years = 25)
allharv_wo <- plot_stoch_harvest(simsout_wo_act,  harvesttype= 1)

antlerless_wo <- plot_stoch_harvest(simsout_wo_act,  harvesttype= 3)

antlerlessplot <- (antlerless_w + antlerless_wo)

ggsave(plot = antlerlessplot, "CWD_model_Cross/MayWorkshopPlots/antlerlessplot.png",
       width = 6, height = 4)


## Let's try setting hunter's take to 20% (aka amount of popn that hunters can remove - set high)
# line 782
# Now see pulses in harvest

abund_wo <- plot_stoch_abundance(simsout_wo_act, all.lines = TRUE, error.bars)
abund_w <- plot_stoch_abundance(simsout_w_act, all.lines = TRUE, error.bars)

abund_w + abund_wo

prev_woAction <- plot_stoch_prev_single(simsout_wo_act$counts, all.lines = TRUE)
prev_wAction <- plot_stoch_prev_single(simsout_w_act$counts, all.lines = TRUE)

prev_wAction + prev_woAction
```



Action_young_bucks
- for each hunting season, takes the number of yearling buckets removed and multiples that 
set to *1.1 but I don't think this is working as expected
```{r young bucks, message = FALSE, warning=FALSE, fig.cap= "Figure 4: Test 'young buck removal' action (with action is on left)"}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(0,0,0,0,0,0,200,0,0,0,0,0,0,0,0,0,0,0,0,0, 0,1,0,0,0), 
             Action_young_bucks = 1, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 460
)

simsout_w_act <- cwd_stoch_wrapper_setARV(params, nsims = 30, n.years = 25)
allharv_w <- plot_stoch_harvest(simsout_w_act,  harvesttype= 1)

juvharv_w <- plot_stoch_harvest(simsout_w_act,  harvesttype= 2, detectbar)
antlerless_w <- plot_stoch_harvest(simsout_w_act, all.lines, error.bars, detectbar, harvesttype= 3)

abund_w <- plot_stoch_abundance(simsout_w_act, all.lines = TRUE, error.bars)


params$Action_young_bucks <- 0

simsout_wo_act <- cwd_stoch_wrapper_setARV(params, nsims = 30, n.years = 25)
allharv_wo <- plot_stoch_harvest(simsout_wo_act,  harvesttype= 1)

juvharv_wo <- plot_stoch_harvest(simsout_wo_act,  harvesttype= 2, all.lines = FALSE, detectbar)
antlerless_wo <- plot_stoch_harvest(simsout_wo_act, all.lines, error.bars, detectbar, harvesttype= 3)

abund_wo <- plot_stoch_abundance(simsout_wo_act, all.lines = TRUE, error.bars)


juvharvplot <- (juvharv_w + juvharv_wo)

ggsave(plot = juvharvplot, "CWD_model_Cross/MayWorkshopPlots/juvharvplot.png",
       width = 6, height = 4)

abund_w + abund_wo


## Let's try upping from 10% to 85% increase in harvest
# line 782
# Now see pulses in harvest
```

### Check arrival times across strategies 
copying function here so can set actions to OFF 
standardize the number of samples across all strategies 

!!!!!!!! These changes won't carry over because source function that sets parameters in foreach loop ***
```{r, message = FALSE, warning=FALSE, fig.cap= "Figure 5: Test arrival times across hypotheses (H1: infected carcass, H2: captive cervid, H3: natural movement, H4: all combined"}

ComHypowSelectH <- function(selectstrat = "SQ", selecthypo = "H1"){
  
  ### Set the parameters based on the selected straetgy 
  if(selectstrat == "SQ" | selectstrat == "SA" | selectstrat == "Ho"){
    params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82, ad.an.m.sur = 0.8,
                   fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
                   hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1, hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                   ini.fawn.prev = 0.01, ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
                   n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                   p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
                   theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
                   repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005, juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005, juv.repro.var = 0.005, ad.repro.var = 0.005,
                   WSI = 1,
                   arrival_input = c(0,0,0,0,0,0,0, 0, 0, 0), 
                   Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
                   nosampled = 100
    )
    if(selectstrat == "Ho"){
      params$nosampled <- 100 ## Need to overwrite number of samples in surviellance strategy tied to Ho
    }
  }else{ # other strategies have hunting actions turned on
    params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82, ad.an.m.sur = 0.8,
                   fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
                   hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1, hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                   ini.fawn.prev = 0.01, ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
                   n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                   p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
                   theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
                   repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005, juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005, juv.repro.var = 0.005, ad.repro.var = 0.005,
                   WSI = 1,
                   arrival_input = c(0,0,0,0,0,0,0, 0, 0, 0), 
                   Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
                   nosampled = 100
    )
    if(selectstrat == "PareR" | selectstrat == "SK"){
      params$nosampled <- 100 ## Need to overwrite number of samples in surviellance strategy tied to PareR and Kitchen Sink
    }
  }
  
simsout4 <- cwd_stoch_wrapper(params, nsims = 10, n.years = 25, strat = selectstrat, hypothesis = selecthypo)
  

  return(simsout4)
}

source("CWD_model_Cross/functions/CompareAltsFuncwSetH_Plot_func.R") # use for multi strat single H

H1 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H1")
H2 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H2")
H3 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H3")
H4 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H4")

H1; H2; H3; H4
```
*I think this shows that we need to turn stochasticity off.. should set each hypothesis as one vector* 



No actions are turned on.. 
Let the number of samples vary across all strategies 
```{r, message = FALSE, warning=FALSE, fig.cap= "Figure 6: Test arrival times across hypotheses (H1: infected carcass, H2: captive cervid, H3: natural movement, H4: all combined"}

ComHypowSelectH <- function(selectstrat = "SQ", selecthypo = "H1"){
  
  ### Set the parameters based on the selected straetgy 
  if(selectstrat == "SQ" | selectstrat == "SA" | selectstrat == "Ho"){
    params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82, ad.an.m.sur = 0.8,
                   fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
                   hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1, hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                   ini.fawn.prev = 0.01, ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
                   n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                   p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
                   theta = 0.9, n0 = 140000, n.years = 25, rel.risk = 1.0,
                   repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005, juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005, juv.repro.var = 0.005, ad.repro.var = 0.005,
                   WSI = 1,
                   arrival_input = c(0,0,0,0,0,0,0, 0, 0, 0), 
                   Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
                   nosampled = 5
    )
    if(selectstrat == "Ho"){
      params$nosampled <- 230 ## Need to overwrite number of samples in surviellance strategy tied to Ho
    }
  }else{ # other strategies have hunting actions turned on
    params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82, ad.an.m.sur = 0.8,
                   fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
                   hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1, hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                   ini.fawn.prev = 0.01, ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
                   n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                   p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
                   theta = 0.9, n0 = 140000, n.years = 25, rel.risk = 1.0,
                   repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005, juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005, juv.repro.var = 0.005, ad.repro.var = 0.005,
                   WSI = 1,
                   arrival_input = c(0,0,0,0,0,0,0, 0, 0, 0), 
                   Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
                   nosampled = 125
    )
    if(selectstrat == "PareR" | selectstrat == "SK"){
      params$nosampled <- 460 ## Need to overwrite number of samples in surviellance strategy tied to PareR and Kitchen Sink
    }
  }
  
simsout4 <- cwd_stoch_wrapper(params, nsims = 10, n.years = 25, strat = selectstrat, hypothesis = selecthypo)
  

  return(simsout4)
}


H1 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H1")
H2 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H2")
H3 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H3")
H4 <- CompareAltsFuncwSetH(setstrats = c("SQ", "Ho", "SK", "NoAA", "PareR", "PventR", "SA"), plottype = "abundance", SetH = "H4")

H1; H2; H3; H4
```







Compare Hypotheses for one strategy (Kitchen Sink)
```{r, eval=FALSE}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(0,0,0,0,0,0,200,0,0,0,0,0,0,0,0,0,0,0,0,0, 0,1,0,0,0), 
             Action_young_bucks = 1, Action_lib_harvest = 1,  Action_sharpshooting = 1,
             nosampled = 460
)

# simsout <- cwd_stoch_model(params)
simsout_H1 <- cwd_stoch_wrapper(params, nsims = 10, n.years = 25, strat = "SK", hypothesis = "H1")
simsout_H2 <- cwd_stoch_wrapper(params, nsims = 50, n.years = 25, strat = "SK", hypothesis = "H2")

simsout_H1 <- cwd_stoch_wrapper_setARV(params, nsims = 10, n.years = 25)

simsout_H1 <- output
H1_prev <- plot_stoch_prev_single(simsout_H1$counts, all.lines = TRUE)
H1_abund <- plot_stoch_abundance(simsout_H1, all.lines = TRUE, error.bars)
H1_harv <- plot_stoch_harvest(simsout_H1, all.lines, error.bars, detectbar, harvesttype= 1)

plot_stoch_harvest(simsout_H1, all.lines, error.bars, detectbar, harvesttype= 2)
plot_stoch_harvest(simsout_H1, all.lines, error.bars, detectbar, harvesttype= 3)


```

