---
title: "Viusal_Action_check"
output: html_document
date: "2024-04-25"
---




set up
```{r}
library(Hmisc)
library(tidyverse)
library(reshape2)
library(foreach)
library(doParallel)

source("functions/est_beta_params.R")
source("functions/allocate_deaths.R")
source("functions/MyFunctions.R")
source("cwd_stoch_model_cal_act.r")
source("ArrivalVectors.R")
source("functions/cwd_stoch_wrapper_mod.r")
```


Run model
```{r}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
               # ini.fawn.prev = (2/10000),
               # ini.juv.prev = (2/10000), ini.ad.f.prev = (2/10000),  ini.ad.m.prev = (2/10000),
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 10, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 1, Action_lib_harvest = 1,  Action_sharpshooting = 1,
             nosampled = 5
)

# simsout <- cwd_stoch_model(params)
simsout <- cwd_stoch_wrapper(params, nsims = 50, n.years, strat, hypothesis)
## Inputs here need to line up.. with params values
```



Get summary stats from arrival vectors 
*Note, things get weird if n.years doesn't = 25
```{r, message=FALSE}
ArrivalVects <- ArrivalVecsFunc(n.years = 25, nsims = 50)
hold <- n.years + 4

ArrivalVects[,5:hold] <- NA

for(i in 1:nrow(ArrivalVects)){
  tempvec <- as.vector(unlist(ArrivalVects$Vec[i]))
  ArrivalVects[i,5:hold] <- t(tempvec)
}

emptyvec <- c()
for(i in 1:25){
  hold <- paste0("time", i)
  if(i == 1){
    emptyvec <- hold
  }else{
      emptyvec <- c(emptyvec, hold)
  }
}

colnames(ArrivalVects) <- c("Strategy" , "Hypo",     "Vec" ,     "sim" , "time1",  "time2",  "time3",  "time4",  "time5",  "time6",  "time7",  "time8", "time9",  "time10", "time11", "time12", "time13", "time14", "time15", "time16", "time17", "time18", "time19", "time20", "time21", "time22" , "time23", "time24",
 "time25")


ArrivalVects_sum <- ArrivalVects %>% 
  dplyr::select(-c(Vec)) %>% 
  group_by(Strategy, Hypo) %>% 
  summarise(across(time1:time25, ~mean(., na.rm = TRUE))) %>% 
  pivot_longer(cols = c("time1",  "time2",  "time3",  "time4",  "time5",  "time6",  "time7",  "time8", "time9",  "time10", "time11", "time12", "time13", "time14", "time15", "time16", "time17", "time18", "time19", "time20", "time21", "time22" , "time23", "time24",
 "time25"), names_to = "time", values_to = "n") %>%
  separate(col = time, into = c("time", "number"), sep = "(?<=time)(?=\\d)")

ArrivalVects_sum$number <- as.numeric(ArrivalVects_sum$number)

ggplot(data = ArrivalVects_sum,
              aes(x = number, y = n)) +
  geom_point(aes(color = Strategy), position = "jitter") +
  facet_wrap(~Hypo)

ArrivalVects_sumH1 <- ArrivalVects_sum %>% 
  filter(Hypo == "H1")
ggplot(data = ArrivalVects_sumH1,
              aes(x = number, y = n)) +
  # geom_point(aes(color = Strategy), position = "jitter") 
  geom_line(aes(color = Strategy)) 


ArrivalVects_sumH2 <- ArrivalVects_sum %>% 
  filter(Hypo == "H2")
ggplot(data = ArrivalVects_sumH2,
              aes(x = number, y = n)) +
  # geom_point(aes(color = Strategy), position = "jitter") 
  geom_line(aes(color = Strategy)) 

ArrivalVects_sumH3 <- ArrivalVects_sum %>% 
  filter(Hypo == "H3")
ggplot(data = ArrivalVects_sumH3,
              aes(x = number, y = n)) +
  # geom_point(aes(color = Strategy), position = "jitter") 
  geom_line(aes(color = Strategy)) 

ArrivalVects_sumH4 <- ArrivalVects_sum %>% 
  filter(Hypo == "H4")
ggplot(data = ArrivalVects_sumH4,
              aes(x = number, y = n)) +
  # geom_point(aes(color = Strategy), position = "jitter") 
  geom_line(aes(color = Strategy)) 




```
Set up as box and wisper plots? Not sure how as working with time series...

Sum of total infected
```{r}
ArrivalVects_mean <- ArrivalVects %>% 
  dplyr::select(-c(Vec)) %>% 
  mutate(TotalInfect = rowSums(select(., starts_with("time")))) %>% 
  group_by(Strategy, Hypo) %>% 
  summarise(mean_TotalInfect = mean(TotalInfect, na.rm = TRUE))

  ArrivalVects_errors <- ArrivalVects %>% 
  dplyr::select(-c(Vec)) %>% 
  mutate(TotalInfect = rowSums(select(., starts_with("time")))) %>% 
  group_by(Strategy, Hypo) %>% 
    dplyr::summarize(lo = quantile(n, 0.025, na.rm=T),
                     hi = quantile(n, 0.975, na.rm=T))
  


ArrivalVects %>% 
   pivot_longer(cols = c("time1",  "time2",  "time3",  "time4",  "time5",  "time6",  "time7",  "time8", "time9",  "time10", "time11", "time12", "time13", "time14", "time15", "time16", "time17", "time18", "time19", "time20", "time21", "time22" , "time23", "time24",
 "time25"), names_to = "time", values_to = "n") %>%
  separate(col = time, into = c("time", "number"), sep = "(?<=time)(?=\\d)") %>% 
  filter(Hypo == "H1") %>% 
ggplot(
              aes(x = Strategy, y = n)) +
  geom_violin() + 
  geom_boxplot(width=0.1) + 
  theme_minimal()

```


```{r}
set_n.years = 25
ArrivalVects <- ArrivalVecsFunc(n.years = set_n.years, nsims = 500)
hold <- set_n.years + 4

ArrivalVects[,5:hold] <- NA

for(i in 1:nrow(ArrivalVects)){
  tempvec <- as.vector(unlist(ArrivalVects$Vec[i]))
  ArrivalVects[i,5:hold] <- t(tempvec)
}

emptyvec <- c()
for(i in 1:25){
  hold <- paste0("time", i)
  if(i == 1){
    emptyvec <- hold
  }else{
      emptyvec <- c(emptyvec, hold)
  }
}

colnames(ArrivalVects) <- c("Strategy" , "Hypo",     "Vec" ,     "sim" , "time1",  "time2",  "time3",  "time4",  "time5",  "time6",  "time7",  "time8", "time9",  "time10", "time11", "time12", "time13", "time14", "time15", "time16", "time17", "time18", "time19", "time20", "time21", "time22" , "time23", "time24",
 "time25")

ArrivalVects2 <- ArrivalVects %>% 
   pivot_longer(cols = c("time1",  "time2",  "time3",  "time4",  "time5",  "time6",  "time7",  "time8", "time9",  "time10", "time11", "time12", "time13", "time14", "time15", "time16", "time17", "time18", "time19", "time20", "time21", "time22" , "time23", "time24",
 "time25"), names_to = "time", values_to = "n") %>%
  separate(col = time, into = c("time", "number"), sep = "(?<=time)(?=\\d)") %>% 
  group_by(sim, Strategy, Hypo) %>% 
  summarise(new_individuals = sum(n))

ggplot(data = ArrivalVects2, aes(x = Strategy, y = new_individuals)) +
  geom_violin() + 
  geom_boxplot(width=0.1) + 
  facet_wrap(~Hypo) + 
  theme_minimal() + 
  labs(x = "Straetgy", 
       y = "Newly infected individuals", 
       title = "Cumulative number of infected individuals over 25 years")



ArrivalVects2$Strategy <- factor(ArrivalVects2$Strategy, labels = c("Heavy Outreach", "No VAAFM", "Prepare and React", "Prevent and React", "Stop Arrival", "Kitchen Sink", "Status Quo"))

### zoom in to H4
arrivalplot_Maypres <- ArrivalVects2 %>% 
  group_by(Strategy, sim) %>% 
  summarise(avg = mean(new_individuals)) %>% 
ggplot(aes(x = Strategy, y = avg)) +
#  geom_violin() + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(x = "Strategy", 
       y = "Newly infected individuals", 
       title = "Cumulative number of newly infected individuals over 25 years",
       caption = "Not including transmission of disease between infected wild deer in state.") +
  ylim(20, 35) + 
  theme(axis.text.x = element_text(angle = -15, hjust = 0), 
        axis.text.y = element_blank(),  # Remove y-axis numbers
        axis.ticks.y = element_blank()) # Remove y-axis ticks



ggsave(plot = arrivalplot_Maypres, "MayWorkshopPlots/arrivalplot.png",
       width = 6, height = 4)

```

First detection vs surveillance programs (stick strategies in then can adjust)
```{r}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 5
)


makedetectiondf_func <- function(setstrategy = "SQ"){
  HypoOptions <- c("H1", "H2", "H3", "H4")
  setstrategy = setstrategy
    tempout <- foreach(i = HypoOptions, .packages = c("dplyr", 
            "tidyr", "stringr", "reshape2")) %dopar% {
            ## Need to load function into loop, might be worth looking into .export          
              source("functions/cwd_stoch_wrapper_mod.r")
              source("functions/est_beta_params.R")
              source("functions/allocate_deaths.R")
              source("functions/MyFunctions.R")
              source("cwd_stoch_model_cal_act.r")
              source("ArrivalVectors.R")
            
            simsout <-  cwd_stoch_wrapper(params, nsims = 150, n.years = 25, strat = setstrategy, hypothesis = i)
              
              detected_prev_sims <- simsout$survillance %>%
                filter(population > 0) %>%
                group_by(sim, year, month) %>%
                summarise(detectedprev_count = n()) %>% 
                group_by(sim) %>%
                summarise(year = min(year)) %>% 
                mutate(hypo = i)
            }
  
  ### Combine lists into one dataset 
    for(i in 1:length(HypoOptions)){
    hold <- tempout[[i]] 
    if(i == 1){
      df <- hold
    }else{
      df <- df %>% full_join(hold)
    }
    }
  df <- df %>% mutate(strat = setstrategy)
  return(df)
}

  
detectSQ <- makedetectiondf_func(setstrategy = "SQ")
detectSA <- makedetectiondf_func(setstrategy = "SA")


params$nosampled <- 125

detectPventR <- makedetectiondf_func(setstrategy = "PventR")
detectNoAA <- makedetectiondf_func(setstrategy = "NoAA")

params$nosampled <- 230
detectHo <- makedetectiondf_func(setstrategy = "Ho")

params$nosampled <- 460
detectPareR <- makedetectiondf_func(setstrategy = "PareR")
detectSK <- makedetectiondf_func(setstrategy = "SK")

## Put into one dataset
detectdf <- detectSQ %>% 
  full_join(detectSA) %>% 
  full_join(detectPventR) %>% 
  full_join(detectNoAA) %>% 
  full_join(detectHo) %>% 
  full_join(detectPareR) %>% 
  full_join(detectSK)

detectdf$strat <- factor(detectdf$strat, levels = c("SQ", "SA", "PventR", "NoAA", "Ho", "PareR", "SK") )

ggplot(data = detectdf, aes(x = strat, y = year)) +
  geom_violin() + 
  geom_boxplot(width=0.1) + 
  theme_minimal() + 
  labs(x = "Straetgy", 
       y = "Year detected", 
       title = "Average year detected",
       caption = "Status Quo sampling of 5 individuals per year [SA, SQ];
 prevalence of 2.5% at 90% confidence was 125 individuals per year [PventR, NoAA]
  prevalence of 1% at 90% confidence was individuals per year 230 [Ho]
 prevalence of 1% at 99% confidence was 460 individuals per year [PareR, KitchenSink - SK]")


ggplot(data = detectdf, aes(x = strat, y = year)) +
  geom_violin() + 
  geom_boxplot(width=0.1) + 
  facet_wrap(~hypo) + 
  theme_minimal() + 
  labs(x = "Straetgy", 
       y = "Year detected", 
       title = "Average year detected",
       caption = "Status Quo sampling of 5 individuals per year [SA, SQ];
 prevalence of 2.5% at 90% confidence was 125 individuals per year [PventR, NoAA]
  prevalence of 1% at 90% confidence was individuals per year 230 [Ho]
 prevalence of 1% at 99% confidence was 460 individuals per year [PareR, KitchenSink - SK]")

```





Difference between arrival and detection vs surveillance programs (stick strategies in then can adjust)
```{r}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 5
)

num_cores <- detectCores() - 3
cl <- makeCluster(num_cores)
registerDoParallel(cl)

makedetectiondf_func <- function(setstrategy = "SQ", setparams = paramshere){
  HypoOptions <- c("H1", "H2", "H3", "H4")
  setstrategy = setstrategy
    tempout <- foreach(i = HypoOptions, .packages = c("dplyr", 
            "tidyr", "stringr", "reshape2")) %dopar% {
            ## Need to load function into loop, might be worth looking into .export          
              # source("CWD_model_Cross/functions/cwd_stoch_wrapper_mod.r")
              # source("CWD_model_Cross/functions/est_beta_params.R")
              # source("CWD_model_Cross/functions/allocate_deaths.R")
              # source("CWD_model_Cross/functions/MyFunctions.R")
              # source("CWD_model_Cross/cwd_stoch_model_cal_act.r")
              # source("CWD_model_Cross/ArrivalVectors.R")
              
              source("functions/cwd_stoch_wrapper_mod.r")
              source("functions/est_beta_params.R")
              source("functions/allocate_deaths.R")
              source("functions/MyFunctions.R")
              source("cwd_stoch_model_cal_act.r")
              source("ArrivalVectors.R")
            
            simsout <-  cwd_stoch_wrapper_linkarrv(params = setparams, nsims = 50, n.years = 25, strat = setstrategy, hypothesis = i)
              
              detected_prev_sims <- simsout$survillance %>%
                filter(population > 0) %>%
                group_by(sim, year, month) %>%
                summarise(detectedprev_count = n()) %>% 
                group_by(sim) %>%
                summarise(year = min(year)) %>% 
                mutate(hypo = i)
              
              df <- data.frame(arrival_input = rep(0, nrow(simsout$ArrivalVec)))
              for(j in 1:nrow(simsout$ArrivalVec)){
                if(sum(unlist(simsout$ArrivalVec$Vec[j])) != 0){
                  df$arrival_yr[j] <- min(which(unlist(simsout$ArrivalVec$Vec[j]) > 0))
                  df$strat[j] <- simsout$ArrivalVec$Strategy[j]
                  df$sim[j] <- simsout$ArrivalVec$sim[j]
                  df$hypo[j] <- simsout$ArrivalVec$Hypo[j]
                }else{
                  df$arrival_yr[j] <- 0
                  df$strat[j] <- simsout$ArrivalVec$Strategy[j]
                  df$sim[j] <- simsout$ArrivalVec$sim[j]
                  df$hypo[j] <- simsout$ArrivalVec$Hypo[j]
                }
              }
              
            here <- df %>% full_join(detected_prev_sims)
            here

              
            }
  
  ### Combine lists into one dataset 
    for(k in 1:length(HypoOptions)){
    hold <- tempout[[k]] 
    if(k == 1){
      df <- hold
    }else{
      df <- df %>% full_join(hold)
    }
    }
  df <- df %>% mutate(strat = setstrategy)
  return(df)
}

  
detectSQ <- makedetectiondf_func(setstrategy = "SQ", setparams =params)

detectSA <- makedetectiondf_func(setstrategy = "SA", setparams =params)


params$nosampled <- 125

detectPventR <- makedetectiondf_func(setstrategy = "PventR", setparams =params)
detectNoAA <- makedetectiondf_func(setstrategy = "NoAA", setparams =params)

params$nosampled <- 230
detectHo <- makedetectiondf_func(setstrategy = "Ho", setparams =params)

params$nosampled <- 460
detectPareR <- makedetectiondf_func(setstrategy = "PareR", setparams =params)
detectSK <- makedetectiondf_func(setstrategy = "SK", setparams =params)

## Put into one dataset
detectdf <- detectSQ %>% 
  full_join(detectSA) %>% 
  full_join(detectPventR) %>% 
  full_join(detectNoAA) %>% 
  full_join(detectHo) %>% 
  full_join(detectPareR) %>% 
  full_join(detectSK)

# remove any runs when it wasn't detected AND didn't arrive
detectdf <- detectdf %>% 
  filter(!(is.na(year) & arrival_yr == 0))

## get count of number of times disease wasn't detected across different strategies 
no_detect <- detectdf %>% 
  group_by(strat) %>% 
  summarise(here = round(((sum(is.na(year)))/n()) * 100)) 
  #get percentage of missed cases


## Get the difference in years from when the disease arrives to when it's detected
detect_arr_diff <- detectdf %>% 
  filter(!(is.na(year))) %>% 
  mutate(diff = year - arrival_yr) %>% 
  mutate(diff = diff - .5) 

detect_arr_diff$strat <- factor(detect_arr_diff$strat, 
  levels = c("SQ", "SA", "PventR", "NoAA", "Ho", "PareR", "SK"), 
  labels = c("Status Quo", "Stop Arrival", "Prevent and React", "No VAAFM", "Heavy Outreach",  "Prepare and React", "Kitchen Sink") )
no_detect$strat <- factor(no_detect$strat, levels = c("SQ", "SA", "PventR", "NoAA", "Ho", "PareR", "SK"), labels = c("Status Quo", "Stop Arrival", "Prevent and React", "No VAAFM", "Heavy Outreach",  "Prepare and React", "Kitchen Sink") )

detectdiffplot_Maypres <- ggplot(data = detect_arr_diff, aes(x = strat, y = diff)) +
  # geom_violin() + 
  geom_boxplot() + 
  geom_text(data = no_detect, aes(x = strat, y = 27, label = here), vjust = 1, color = "red") +
  theme_minimal()+ 
  labs(x = "Straetgy", 
       y = "Delay in detection post arrival", 
       title = "Average year detected",
 #       caption = "Status Quo sampling of 5 individuals per year [SA, SQ];
 # prevalence of 2.5% at 90% confidence was 125 individuals per year [PventR, NoAA]
 #  prevalence of 1% at 90% confidence was individuals per year 230 [Ho]
 # prevalence of 1% at 99% confidence was 460 individuals per year [PareR, KitchenSink - SK]
 # The red numbers how frequently there was no detection after the disease arrived (%)")
 caption = "The red numbers are how frequently there was no detection after the disease arrived (%)") +
  theme(axis.text.x = element_text(angle = -15, hjust = 0)) 

ggsave(plot = detectdiffplot_Maypres, "MayWorkshopPlots/detectdifplot.png",
       width = 6, height = 4)

```






Difference between arrival and detection vs surveillance programs 
*plot as probability of detection by year* 

```{r}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 5
)

num_cores <- detectCores() - 3
cl <- makeCluster(num_cores)
registerDoParallel(cl)

makedetectiondf_func <- function(setstrategy = "SQ", setparams = paramshere){
  HypoOptions <- c("H1", "H2", "H3", "H4")
  setstrategy = setstrategy
    tempout <- foreach(i = HypoOptions, .packages = c("dplyr", 
            "tidyr", "stringr", "reshape2")) %dopar% {
            ## Need to load function into loop, might be worth looking into .export          
              # source("CWD_model_Cross/functions/cwd_stoch_wrapper_mod.r")
              # source("CWD_model_Cross/functions/est_beta_params.R")
              # source("CWD_model_Cross/functions/allocate_deaths.R")
              # source("CWD_model_Cross/functions/MyFunctions.R")
              # source("CWD_model_Cross/cwd_stoch_model_cal_act.r")
              # source("CWD_model_Cross/ArrivalVectors.R")
              
              source("functions/cwd_stoch_wrapper_mod.r")
              source("functions/est_beta_params.R")
              source("functions/allocate_deaths.R")
              source("functions/MyFunctions.R")
              source("cwd_stoch_model_cal_act.r")
              source("ArrivalVectors.R")
            
            simsout <-  cwd_stoch_wrapper_linkarrv(params = setparams, nsims = 50, n.years = 25, strat = setstrategy, hypothesis = i)
              
              detected_prev_sims <- simsout$survillance %>%
                filter(population > 0) %>%
                group_by(sim, year, month) %>%
                summarise(detectedprev_count = n()) %>% 
                group_by(sim) %>%
                summarise(year = min(year)) %>% 
                mutate(hypo = i)
              
              df <- data.frame(arrival_input = rep(0, nrow(simsout$ArrivalVec)))
              for(j in 1:nrow(simsout$ArrivalVec)){
                if(sum(unlist(simsout$ArrivalVec$Vec[j])) != 0){
                  df$arrival_yr[j] <- min(which(unlist(simsout$ArrivalVec$Vec[j]) > 0))
                  df$strat[j] <- simsout$ArrivalVec$Strategy[j]
                  df$sim[j] <- simsout$ArrivalVec$sim[j]
                  df$hypo[j] <- simsout$ArrivalVec$Hypo[j]
                }else{
                  df$arrival_yr[j] <- 0
                  df$strat[j] <- simsout$ArrivalVec$Strategy[j]
                  df$sim[j] <- simsout$ArrivalVec$sim[j]
                  df$hypo[j] <- simsout$ArrivalVec$Hypo[j]
                }
              }
              
            here <- df %>% full_join(detected_prev_sims)
            here

              
            }
  
  ### Combine lists into one dataset 
    for(k in 1:length(HypoOptions)){
    hold <- tempout[[k]] 
    if(k == 1){
      df <- hold
    }else{
      df <- df %>% full_join(hold)
    }
    }
  df <- df %>% mutate(strat = setstrategy)
  return(df)
}

  
detectSQ <- makedetectiondf_func(setstrategy = "SQ", setparams =params)

detectSA <- makedetectiondf_func(setstrategy = "SA", setparams =params)


params$nosampled <- 125

detectPventR <- makedetectiondf_func(setstrategy = "PventR", setparams =params)
detectNoAA <- makedetectiondf_func(setstrategy = "NoAA", setparams =params)

params$nosampled <- 230
detectHo <- makedetectiondf_func(setstrategy = "Ho", setparams =params)

params$nosampled <- 460
detectPareR <- makedetectiondf_func(setstrategy = "PareR", setparams =params)
detectSK <- makedetectiondf_func(setstrategy = "SK", setparams =params)

## Put into one dataset
detectdf <- detectSQ %>% 
  full_join(detectSA) %>% 
  full_join(detectPventR) %>% 
  full_join(detectNoAA) %>% 
  full_join(detectHo) %>% 
  full_join(detectPareR) %>% 
  full_join(detectSK)

# remove any runs when it wasn't detected AND didn't arrive
detectdf <- detectdf %>% 
  filter(!(is.na(year) & arrival_yr == 0))

detectdf[which(is.na(detectdf$year)),6] <- 46.5

## get count of number of times disease wasn't detected across different strategies 
detectdf_mod <- detectdf %>% 
  group_by(strat) %>% 
  mutate(diff = year - arrival_yr) %>% 
  mutate(diff = diff + .5) %>% 
  count(diff) %>%
  mutate(probability = n / sum(n),
            cumulative_probability = cumsum(probability)) %>% 
  # but we only care about values up to 25
  filter(diff <= 25)



detectdf_mod$strat <- factor(detectdf_mod$strat, 
  levels = c("SQ", "SA", "PventR", "NoAA", "Ho", "PareR", "SK"), 
  labels = c("Status Quo", "Stop Arrival", "Prevent and React", "No VAAFM", "Heavy Outreach",  "Prepare and React", "Kitchen Sink") )

detectdiffplot_Maypres <- ggplot(data = detectdf_mod, aes(x = diff, y = cumulative_probability)) +
  geom_line(aes(color = strat)) +
  theme_minimal()+ 
  labs(x = "Time (Years)", 
       y = "Cumulative Probability of Detection", 
       title = "Time from arrival to detection (Years)",
       color = "Strategy") 

ggsave(plot = detectdiffplot_Maypres, "MayWorkshopPlots/detectdifplot.png",
       width = 6, height = 4)

```




Heavy Outreach (Ho), Stop Arrival (SA), and Status Quo (SQ) have NO hunting actions
Prevent and React (PventR), Prepare and React (PareR) and No VAAFM (NoAA) have ALL hunting actions
number of individuals sampled is determined by strategy 
 statquosamp <- 5 [SA, SQ]
 prv2.5_90samp <- 125 [PventR, NoAA]
 prv1_99samp <- 460 [PareR, KitchenSink - SK]
 prv1_90samp <- 230 #[Ho]


```{r Stat Quo}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 25, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 0, Action_lib_harvest = 0, Action_sharpshooting = 0,
             nosampled = 5
)

# simsout <- cwd_stoch_model(params)
simsout <- cwd_stoch_wrapper(params, nsims = 50, n.years = 25, strat = "SQ", hypothesis = "H1")
## Inputs here need to line up.. with params values

plot_stoch_prev_single(simsout$counts, all.lines = TRUE)
plot_stoch_abundance(simsout, all.lines = TRUE, error.bars)
plot_stoch_harvest(simsout, all.lines, error.bars, detectbar, harvesttype= 1)
```

Values need for the consequence table.. 
```{r}
### detection time stamp
detection_time_func <- function(dat){
    detected_prev <- dat$survillance %>%
    filter(population > 0) %>%
    group_by(sim, year, month) %>%
    summarise(detectedprev_count = n()) %>% 
    group_by(sim) %>%
    summarise(min_year = min(year))
  
  Avg_min_year = mean(detected_prev$min_year) # this is the average value 
  return(Avg_min_year)
}
detection_time(simsout)

### Spread/prevalence - The true state of percent prevalence of CWD after 25 years 
prev_func <- function(dat){
final_prev <- dat$counts %>%
  filter(month %% 12 == 1) %>%
  group_by(year, disease) %>%
  summarise(n = sum(population), .groups = "drop") %>%
  spread(key = disease, value = n) %>%
  mutate(prev = yes / (no + yes)) %>%
  arrange(desc(year)) %>%
  slice(1) %>%
  select(prev)
return(final_prev)
}

### Average size of the deer population over 25 years (“Population”)
#!!! Check the way the averaging is set up here... !!!

detection_time <- function(dat){
  dat.counts <- dat$counts
  dat.sum <- dat.counts %>%
    filter(month %% 12 == 11) %>%
    group_by(year) %>%
    dplyr::summarize(n = sum(population)) %>% 
    dplyr::summarize(avg = mean(n, na.rm = T))
  return(dat.sum)
}

```



```{r Heavy Outreach}
params <- list(fawn.an.sur = 0.7, juv.an.sur = 0.8, ad.an.f.sur = 0.82,
               ad.an.m.sur = 0.8, fawn.repro = 0.06, juv.repro = 1.3, ad.repro = 1.4,
               hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1,
               hunt.mort.ad.f = 0.12, hunt.mort.ad.m = 0.50,
                ini.fawn.prev = 0.01,
                ini.juv.prev = 0.03, ini.ad.f.prev = 0.04,  ini.ad.m.prev = 0.04,
               n.age.cats = 12,  n.age.cats.m = 10, n.age.cats.f = 15,
                p = 0.27, env.foi = 0,  beta.f = 0.028,  beta.m = 0.028,
               theta = 0.9, n0 = 10000, n.years = 10, rel.risk = 1.0,
               repro.var = 0.005, fawn.sur.var = 0.005, sur.var = 0.005, hunt.var = 0.0005,
               juv.sur.var = 0.005, ad.f.sur.var = 0.005, ad.m.sur.var = 0.005,
             juv.repro.var = 0.005, ad.repro.var = 0.005,
             WSI = 1,
             arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), 
             Action_young_bucks = 0, Action_lib_harvest = 0,  Action_sharpshooting = 0,
             nosampled = 5
)

# simsout <- cwd_stoch_model(params)
simsout <- cwd_stoch_wrapper(params, nsims = 50, n.years = 25, strat = "SQ", hypothesis = "H1")
## Inputs here need to line up.. with params values

plot_stoch_prev_single(simsout$counts, all.lines = TRUE)
plot_stoch_abundance(simsout, all.lines = TRUE, error.bars)
plot_stoch_harvest(simsout, all.lines, error.bars, detectbar, harvesttype= 1)
```



