---
title: "Calibrate SII Model"
author: "Annabelle"
date: "2024-11-20"
output: html_document
---

***Outstanding notes/questions***

- Note, assuming that the population model starts in spring (month when fawns are born)

### Calibration graphs shown 
- Abundance [all, bucks, does, fawns]
- Doe:Fawn ratio 
- Harvest [buck, doe, juvenile, fawn]
- Survival [adult, juvenile, fawn]

Load libraries and files 
```{r, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(here)
library(reshape2)

source("../SII_model/functions/CreateStableAgeStructure_func.R")
source("../SII_model/functions/popnmodel_func.R")
source("../SII_model/functions/sims_wrapper_func.R")
source("../SII_model/functions/randomsampling_func.R")

```

- then need to see how did surveillance and actions in old model 
- Should probably update overleaf/latex doc

Set parameters
- Note - can't set repro higher than 1.9 because pulling from a beta distribution (currently using a hack where we divide by 2). Do we want to switch to a gamma? 
```{r}
params <- list(
  fawn.an.sur = 0.7, fawn.an.sur.var= 0.005, juv.f.an.sur = 0.8, juv.f.an.sur.var=0.005, juv.m.an.sur = .8, juv.m.an.sur.var=0.005, ad.an.f.sur = 0.87, ad.an.f.sur.var=0.005, ad.an.m.sur = 0.75, ad.an.m.sur.var=0.005,
  
  juv.repro = 2.6, ad.repro = 2.8,   repro.var = 0.005,
  
  hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.1, hunt.mort.ad.f = 0.2, hunt.mort.ad.m = 0.45, hunt.var = 0.005,
  
  # turn stochasticity of vital rates on and off.. 
    switch_stoch_survival_rates = 1, # (on = 1)
    switch_stoch_hunt_rates = 1, # (on = 1)
    switch_stoch_repro_rates = 1, # (on = 1)
  
  # temp set these to 0 for calibration
  switchdiseasedy_on = 0, # turn disease dynamics on or off (on = 1)
  arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), # currently set for 10 years 
  
  i.rate = .5,
  env = 0, shedrate_I = .5, shedrate_H = .5, shedrate_ND = .5, expdecayconstant = .55, beta = .4,
  
  #model 1
  model1 = 1, # this selects set up for Vasilyeva et al. paper
   ke = .1, lambda = .1, Pe = .1, sigma = .1,
  #model 2?
  ## ???
  
  nyears = 200, n0 = 143000, K = 250000,
  
  ### Action parameters
  nosampled = 5,
  
  
  ### Farm Years - comodel 
  alpha = .01, beta1 = .3, beta2 = .3, beta3 = .3
  )
```





```{r}
popfit <- sims_wrapper(params,  1)

counts_overtime <- as.data.frame(popfit$counts)

harvest_overtime <- as.data.frame(popfit$harvest)
```



#### Check vital rates


survival 
```{r}
vitals_sims_sur <- as.data.frame(popfit$vitalscheck[c(-1),c(1:5,9,10)])
names(vitals_sims_sur) <- c("fawn.sur", "juv.f.sur", "juv.m.sur", "ad.f.sur", "ad.m.sur",
                        "year", "sim")

ggplot(vitals_sims_sur) +
  geom_line(aes(x = year, y = fawn.sur, group = sim), color = "blue", size = 0.5) +  
    geom_line(aes(x = year, y = juv.f.sur, group = sim), color = "red", size = 0.5) +  
    geom_line(aes(x = year, y = juv.m.sur, group = sim), color = "green", size = 0.5) +  
    geom_line(aes(x = year, y = ad.f.sur, group = sim), color = "black", size = 0.5) +  
    geom_line(aes(x = year, y = ad.m.sur, group = sim), color = "grey", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Survival by age category", 
       x = "Year", 
       y = "Survival") 


```


reproduction rate 
```{r}
vitals_sims <- as.data.frame(popfit$vitalscheck[c(-1),c(6:7,9,10)])
names(vitals_sims) <- c("juv.repro", "ad.repro",
                        "year", "sim")

ggplot(vitals_sims) +
  geom_line(aes(x = year, y = juv.repro, group = sim), color = "blue", size = 0.5) +  
    geom_line(aes(x = year, y = ad.repro, group = sim), color = "green", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Reproduction rate by age category", 
       x = "Year", 
       y = "reproduction") 
```

check autocorrelation on ad.repro.draw
https://www.r-bloggers.com/2024/07/calculating-autocorrelation-in-r/
"A high autocorrelation at lag 0 indicates that a variable is highly correlated with itself."
```{r}
acf(vitals_sims$ad.repro[1:10], pl=FALSE)
```


Carrying Capacity 
```{r}
vitals_sims <- as.data.frame(popfit$vitalscheck[c(-1),c(8,9,10)])
names(vitals_sims) <- c("CarryingCap",
                        "year", "sim")

ggplot(vitals_sims) +
  geom_line(aes(x = year, y = CarryingCap, group = sim), color = "grey", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Carrying Capacity over time", 
       x = "Year", 
       y = "N/K") 
```


#### Abundance 


```{r Total Abundance}
dat.sum <- counts_overtime %>%
  group_by(sim, year) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +  
  geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Total Abundance", 
       x = "Year", 
       y = "Total Count") 
```



```{r Abundance for all bucks}
dat.sum.bucks <- counts_overtime %>%
  group_by(sim, year) %>% 
  select(matches("ad.m", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.bucks, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 27729, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Buck Abundance", 
       x = "Year", 
       y = "Total Count") 
```

```{r Abundance for all does}
dat.sum.doe <- counts_overtime %>%
  group_by(sim, year) %>% 
  select(matches("ad.f", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.doe, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 70710, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Doe Abundance", 
       x = "Year", 
       y = "Total Count") 
```


```{r Abundance for all fawns}
dat.sum.fawn <- counts_overtime %>%
  group_by(sim, year) %>% 
  select(matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.fawn, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Fawn Abundance", 
       x = "Year", 
       y = "Total Count") 
```

#### Back calculate age proportion 
```{r}
dat.sum.prop  <- counts_overtime %>%
  mutate(fawn_sum = rowSums(select(., matches("fawn", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(female_sum = rowSums(select(., matches("\\.f\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(male_sum = rowSums(select(., matches("\\.m\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  group_by(sim, year) %>% 
  mutate(total_pop = fawn_sum + female_sum+ male_sum) %>% 
  mutate(fawn_prop = fawn_sum/total_pop) %>% 
  mutate(female_prop = female_sum/total_pop) %>% 
  mutate(male_prop = male_sum/total_pop)

# get average across all sims
dat.sum.prop_avg  <- dat.sum.prop %>%
  # Now group by year only to average across simulations
  group_by(year) %>%
  summarize(
    avg_fawn_prop = mean(fawn_prop, na.rm = TRUE),
    avg_female_prop = mean(female_prop, na.rm = TRUE),
    avg_male_prop = mean(male_prop, na.rm = TRUE),
    .groups = "drop"  # ungroup after summarizing
  )




ggplot(data = dat.sum.prop) +
  geom_line(aes(x = year, y = fawn_prop, group = sim), color = "red") +  
  geom_line(aes(x = year, y = female_prop, group = sim), color = "lightblue") +  
  geom_line(aes(x = year, y = male_prop, group = sim), color = "green") +  
  
  geom_line(data = dat.sum.prop_avg, aes(x = year, y = avg_fawn_prop), color = "darkred") +  
  geom_line(data = dat.sum.prop_avg, aes(x = year, y = avg_female_prop), color = "darkblue") +  
  geom_line(data = dat.sum.prop_avg, aes(x = year, y = avg_male_prop), color = "darkgreen") +  
  #geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Proportional Abundance", 
       x = "Year", 
       y = "Proportion") 
# Goal: fawns = 30%, does = 50%, bucks = 20% 
```



#### Doe:Fawn ratio 
```{r}
doe_fawn_ratio <- counts_overtime %>%
  group_by(sim, year) %>% 
  select(matches("ad.f", ignore.case = TRUE), matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n_doe = rowSums(across(matches("ad.f", ignore.case = TRUE)), na.rm = TRUE))%>%
    dplyr::mutate(n_fawn = rowSums(across(matches("fawn", ignore.case = TRUE)), na.rm = TRUE))%>%
  dplyr::mutate(doe_fawn = n_doe/n_fawn)

ggplot(data = doe_fawn_ratio, aes(x = year, y = doe_fawn)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  geom_hline(yintercept = 1.5, color = "red") + ## This will depend on pop starting size and starting month
  labs(title = "Doe:Fawn Ratio", 
       x = "Year", 
       y = "Total Count")
```




#### Harvest [buck, doe, juv, fawn]

* just a note that if we are going to add complexity to the model, I don't know that the harvest df is set up correctly in the model (would be subject to stochasticity ... currently calculated based on a flat rate)

```{r Harvest for all}
harv.sum <- harvest_overtime %>%
  group_by(sim, year) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Total Harvest", 
       x = "Year", 
       y = "Total Count") 
```

```{r Harvest for all bucks}
harv.sum.bucks <- harvest_overtime %>%
  group_by(sim, year) %>% 
  select(matches("ad.m", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.bucks, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  geom_hline(yintercept = 9600, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 9600 * .1 + 9600, color = "midnightblue") + ## 10% wounding loss + harvest
  labs(title = "Buck Harvest", 
       x = "Year", 
       y = "Total Count") 
```

```{r Harvest for all does}
harv.sum.doe <- harvest_overtime %>% 
  group_by(sim, year) %>% 
  select(matches("ad.f", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.doe, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 6000, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 6000 * .1 + 6000, color = "midnightblue") + ## 10% wounding loss + harvest
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Doe Harvest", 
       x = "Year", 
       y = "Total Count") 
```

juveniles

```{r Harvest for all juveniles}
harv.sum.juv <- harvest_overtime %>%
  group_by(sim, year) %>% 
  select(matches("juv", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.juv, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 3680, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 3680 * .1 + 3680, color = "midnightblue") + ## 10% wounding loss + harvest
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Juveniles Harvest", 
       x = "Year", 
       y = "Total Count") 
```

```{r Harvest for all fawns}
harv.sum.fawn <- harvest_overtime %>%
  group_by(sim,year) %>% 
  select(matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.fawn, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +   
  geom_hline(yintercept = 550, color = "red") + ## This will depend on pop starting size
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Fawn Harvest", 
       x = "Year", 
       y = "Total Count") 
```


#### Survival [adult, juv, fawn]

```{r Survival bucks}
dat.sum.bucks <- counts_overtime %>%
  group_by(sim, year) %>% 
  select(matches("ad.m", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

harv.sum.bucks

ggplot(data = dat.sum.bucks, aes(x = year, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +   
 # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Buck Abundance", 
       x = "Year", 
       y = "Total Count") 
```





#### Disease dynamics 


```{r}
dat.disease.prop  <- counts_overtime %>%
  mutate(suseptible_sum = rowSums(select(., matches("\\.S\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(exposed_sum = rowSums(select(., matches("\\.E\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(infected_sum = rowSums(select(., matches("\\.I\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
      group_by(sim, year) %>% 
  mutate(total_pop = suseptible_sum + exposed_sum+ infected_sum) %>% 
  mutate(suseptible_prop = suseptible_sum/total_pop) %>% 
  mutate(exposed_prop = exposed_sum/total_pop) %>% 
  mutate(infected_prop = infected_sum/total_pop) 


ggplot(data = dat.disease.prop) +
  geom_line(aes(x = year, y = suseptible_prop, group = sim), color = "red") +  
  geom_line(aes(x = year, y = exposed_prop, group = sim), color = "blue") +  
  geom_line(aes(x = year, y = infected_prop, group = sim), color = "green") +  
  #geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Proportional Abundance", 
       x = "Year", 
       y = "Proportion") 
```


Estimate R0
```{r}

```




Other calibration parameters??




