---
title: "Calibrate SII Model"
author: "Annabelle"
date: "2024-11-20"
output: html_document
---

Load libraries and files 
```{r, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(here)
library(reshape2)

source("../SII_model/functions/CreateStableAgeStructure_func.R")
source("../SII_model/functions/popnmodel_func_JC.R")
source("../SII_model/functions/sims_wrapper_func.R")
source("../SII_model/functions/randomsampling_func.R")

```

Define parameter values
```{r}
burnin.int <- 25
myears <- 25
ntotal <- myears + burnin.int

params <- list(
  nyears = myears + burnin.int, #number of simulation years
  burnin = rep(0, times=burnin.int),
  K = 325000,
  alpha.cc = 1,     #controls density dependence
  beta.cc = 1,      #controls density dependence
  fawn.an.sur = 0.7, 
  fawn.an.sur.var= 0.0005, 
  juv.f.an.sur = 0.8, 
  juv.f.an.sur.var=0.0005, 
  juv.m.an.sur = .8, 
  juv.m.an.sur.var=0.0005, 
  ad.an.f.sur = 0.87, 
  ad.an.f.sur.var=0.0005, 
  ad.an.m.sur = 0.75, 
  ad.an.m.sur.var=0.0005,
  juv.repro = 1.5, 
  ad.repro = 1.7,   
  repro.var = 0.005,
  
  #harvest rates from VFWD 2019-2023
  hunt.mort.fawn = 0.05, 
  hunt.mort.juv.f = 0.1, 
  hunt.mort.juv.m = 0.2, 
  hunt.mort.ad.f = 0.1, 
  hunt.mort.ad.m = 0.3, 
  hunt.fawn.var = 7.21314E-05, 
  hunt.var = 0.0003,
  
  i.rate = .5,
  env = 0, 
  shedrate_I = .005, 
  shedrate_H = .5, 
  shedrate_ND = .5, 
  expdecayconstant = 10.5, 
  beta.d.min = 0.75, # roughly from Jennelle et al. 2014.
  beta.d.max=1.5,   # roughly from Jennelle et al. 2014.
  beta.e.min = 0.00000015, 
  beta.e.max= 0.0000015,
  # arrival_input = c(100,100,1,1,1,1,5, 1, 8, 14), # currently set for 10 years 
  arrival_input = c(200,0,0,0,0,0,0,0,0,0),
  additive.dz.mort = 0.2, #xx% higher mortality for juvs, d
  
  ### Farm Years - comodel #JC - this needs updated and described.
  alpha = .01, 
  beta1 = .3, 
  beta2 = .3, 
  beta3 = .3,
  
  #model 1
  model1 = 1, # this selects set up for Vasilyeva et al. paper
  ke = .1, 
  lambda = .1, 
  Pe = .1, 
  sigma = .1,
  
  # turn stochasticity of vital rates on and off.. 
  switch_stoch_survival_rates = 1, # (on = 1)
  switch_stoch_hunt_rates = 1, # (on = 1)
  switch_stoch_repro_rates = 1, # (on = 1)
  
  # temp set these to 0 for calibration
  switchdiseasedy_on = 1, # turn disease dynamics on or off (on = 1)
  
  ### Action parameters
  nosampled = 5,
  Action_young_bucks = 0
  )

list2env(params,globalenv())
```

Run model and create data frames
```{r}
nsims <- 100

popfit <- sims_wrapper(params, nsims)

#remove burned years
counts_overtime.raw <- as.data.frame(popfit$counts)

counts_overtime <- counts_overtime.raw %>%
  filter(year>burnin.int) %>%
  mutate(modelyrs = year-burnin.int)

harvest_overtime.raw <- as.data.frame(popfit$harvest)

harvest_overtime <- harvest_overtime.raw %>%
  filter(year>burnin) %>%
  mutate(modelyrs = year-burnin.int)

```

Total Abundance 
```{r Total Abundance}
dat.sum <- counts_overtime %>%
  group_by(sim, modelyrs) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +  
  geom_hline(yintercept = 147939, color = "red") + #changed red line to average btwn 2019-2023
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))
  labs(title = "Total Abundance", 
       x = "Year", 
       y = "Total Count") 
```

CWD Dynamics
```{r}
dat.disease.prop  <- counts_overtime %>%
  mutate(suseptible_sum = rowSums(select(., matches("\\.S\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(exposed_sum = rowSums(select(., matches("\\.E\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(infected_sum = rowSums(select(., matches("\\.I\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
      group_by(sim, modelyrs) %>% 
  mutate(total_pop = suseptible_sum + exposed_sum+ infected_sum) %>% 
  mutate(suseptible_prop = suseptible_sum/total_pop) %>% 
  mutate(exposed_prop = exposed_sum/total_pop) %>% 
  mutate(infected_prop = infected_sum/total_pop) 


ggplot(data = dat.disease.prop) +
  geom_line(aes(x = modelyrs, y = suseptible_prop, group = sim), color = "red") +  
  geom_line(aes(x = modelyrs, y = exposed_prop, group = sim), color = "blue") +  
  geom_line(aes(x = modelyrs, y = infected_prop, group = sim), color = "green") +  
  #geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Proportional Abundance", 
       x = "Year", 
       y = "Proportion") 
```

### Calibration graphs shown 
- Survival [adult, juvenile, fawn]
- Reproduction [juvenile, adult]
- Reproduction scalar (N/K)
- Abundance [bucks, does, fawns]
- Age proportion
- Doe:Fawn ratio 
- Harvest [buck, doe, juvenile, fawn]

Survival [adult, juvenile, fawn]
```{r}
vitals_sims_sur <- as.data.frame(popfit$vitalscheck[c(-1),c(1:5,9,10)])
names(vitals_sims_sur) <- c("fawn.sur", "juv.f.sur", "juv.m.sur", "ad.f.sur", "ad.m.sur",
                        "year", "sim")

ggplot(vitals_sims_sur) +
  geom_line(aes(x = year, y = fawn.sur, group = sim), color = "blue", size = 0.5) +  
    geom_line(aes(x = year, y = juv.f.sur, group = sim), color = "red", size = 0.5) +  
    geom_line(aes(x = year, y = juv.m.sur, group = sim), color = "green", size = 0.5) +  
    geom_line(aes(x = year, y = ad.f.sur, group = sim), color = "black", size = 0.5) +  
    geom_line(aes(x = year, y = ad.m.sur, group = sim), color = "grey", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Survival by age category", 
       x = "Year", 
       y = "Survival") 
```


Reproduction [juvenile, adult] 
```{r}
vitals_sims <- as.data.frame(popfit$vitalscheck[c(-1),c(6:7,9,10)])
names(vitals_sims) <- c("juv.repro", "ad.repro",
                        "year", "sim")

ggplot(vitals_sims) +
  geom_line(aes(x = year, y = juv.repro, group = sim), color = "blue", size = 0.5) +  
    geom_line(aes(x = year, y = ad.repro, group = sim), color = "green", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Reproduction rate by age category", 
       x = "Year", 
       y = "reproduction") 
```

Carrying Capacity 
```{r}
vitals_sims <- as.data.frame(popfit$vitalscheck[c(-1),c(8,9,10)])
names(vitals_sims) <- c("CarryingCap",
                        "year", "sim")

ggplot(vitals_sims) +
  geom_line(aes(x = year, y = CarryingCap, group = sim), color = "grey", size = 0.5) +  
  # geom_hline(yintercept = 143758, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Carrying Capacity over time", 
       x = "Year", 
       y = "N/K") 
```

Abundance [bucks]
```{r Abundance for all bucks}
dat.sum.bucks <- counts_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("ad.m", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.bucks, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 27729, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Buck Abundance", 
       x = "Year", 
       y = "Total Count") 
```

Abundance [does]
```{r Abundance for all does}
dat.sum.doe <- counts_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("ad.f", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.doe, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 70710, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Doe Abundance", 
       x = "Year", 
       y = "Total Count") 
```

Abundance [fawns]
```{r Abundance for all fawns}
dat.sum.fawn <- counts_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = dat.sum.fawn, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Fawn Abundance", 
       x = "Year", 
       y = "Total Count") 
```

Age proportion
```{r}
dat.sum.prop  <- counts_overtime %>%
  mutate(fawn_sum = rowSums(select(., matches("fawn", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(female_sum = rowSums(select(., matches("\\.f\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  mutate(male_sum = rowSums(select(., matches("\\.m\\.", ignore.case = TRUE)), na.rm = TRUE)) %>%
  group_by(sim, modelyrs) %>% 
  mutate(total_pop = fawn_sum + female_sum+ male_sum) %>% 
  mutate(fawn_prop = fawn_sum/total_pop) %>% 
  mutate(female_prop = female_sum/total_pop) %>% 
  mutate(male_prop = male_sum/total_pop)

# get average across all sims
dat.sum.prop_avg  <- dat.sum.prop %>%
  # Now group by year only to average across simulations
  group_by(modelyrs) %>%
  summarize(
    avg_fawn_prop = mean(fawn_prop, na.rm = TRUE),
    avg_female_prop = mean(female_prop, na.rm = TRUE),
    avg_male_prop = mean(male_prop, na.rm = TRUE),
    .groups = "drop"  # ungroup after summarizing
  )

ggplot(data = dat.sum.prop) +
  geom_line(aes(x = modelyrs, y = fawn_prop, group = sim), color = "red") +  
  geom_line(aes(x = modelyrs, y = female_prop, group = sim), color = "lightblue") +  
  geom_line(aes(x = modelyrs, y = male_prop, group = sim), color = "green") +  
  
  geom_line(data = dat.sum.prop_avg, aes(x = modelyrs, y = avg_fawn_prop), color = "darkred") +  
  geom_line(data = dat.sum.prop_avg, aes(x = modelyrs, y = avg_female_prop), color = "darkblue") +  
  geom_line(data = dat.sum.prop_avg, aes(x = modelyrs, y = avg_male_prop), color = "darkgreen") +  
  #geom_hline(yintercept = 43127, color = "red") +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Proportional Abundance", 
       x = "Year", 
       y = "Proportion") 
# Goal: fawns = 30%, does = 50%, bucks = 20% 
```

Doe:Fawn ratio 
```{r}
doe_fawn_ratio <- counts_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("ad.f", ignore.case = TRUE), matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n_doe = rowSums(across(matches("ad.f", ignore.case = TRUE)), na.rm = TRUE))%>%
    dplyr::mutate(n_fawn = rowSums(across(matches("fawn", ignore.case = TRUE)), na.rm = TRUE))%>%
  dplyr::mutate(doe_fawn = n_doe/n_fawn)

ggplot(data = doe_fawn_ratio, aes(x = modelyrs, y = doe_fawn)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  geom_hline(yintercept = 1.5, color = "red") + ## This will depend on pop starting size and starting month
  labs(title = "Doe:Fawn Ratio", 
       x = "Year", 
       y = "Total Count")
```

Harvest [buck, doe, juv, fawn]
* just a note that if we are going to add complexity to the model, I don't know that the harvest df is set up correctly in the model (would be subject to stochasticity ... currently calculated based on a flat rate)
```{r Harvest for all}
harv.sum <- harvest_overtime %>%
  group_by(sim, modelyrs) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Total Harvest", 
       x = "Year", 
       y = "Total Count") 
```

```{r Harvest for all bucks}
harv.sum.bucks <- harvest_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("ad.m", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.bucks, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  geom_hline(yintercept = 9600, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 9600 * .1 + 9600, color = "midnightblue") + ## 10% wounding loss + harvest
  labs(title = "Buck Harvest", 
       x = "Year", 
       y = "Total Count") 
```

```{r Harvest for all does}
harv.sum.doe <- harvest_overtime %>% 
  group_by(sim, modelyrs) %>% 
  select(matches("ad.f", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.doe, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 6000, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 6000 * .1 + 6000, color = "midnightblue") + ## 10% wounding loss + harvest
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Doe Harvest", 
       x = "Year", 
       y = "Total Count") 
```

Juvenile Harvest
```{r Harvest for all juveniles}
harv.sum.juv <- harvest_overtime %>%
  group_by(sim, modelyrs) %>% 
  select(matches("juv", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.juv, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) + 
  geom_hline(yintercept = 3680, color = "red") + ## This will depend on pop starting size
  geom_hline(yintercept = 3680 * .1 + 3680, color = "midnightblue") + ## 10% wounding loss + harvest
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Juveniles Harvest", 
       x = "Year", 
       y = "Total Count") 
```

Fawn Harvest
```{r Harvest for all fawns}
harv.sum.fawn <- harvest_overtime %>%
  group_by(sim,modelyrs) %>% 
  select(matches("fawn", ignore.case = TRUE)) %>% 
  dplyr::mutate(n = rowSums(across(everything()), na.rm = TRUE))

ggplot(data = harv.sum.fawn, aes(x = modelyrs, y = n)) +
  geom_line(aes(group = sim), color = "grey", size = 0.5) +   
  geom_hline(yintercept = 550, color = "red") + ## This will depend on pop starting size
  theme(axis.text=element_text(size=16), axis.title=element_text(size=20))+
  labs(title = "Fawn Harvest", 
       x = "Year", 
       y = "Total Count") 
```
