---
title: "Population Model Set up"
author: "Annabelle"
date: "2024-09-02"
output: word_document
---

Parameters set in the model 

Age/Sex/Disease 

```{r}
## Suseptible
#' fawn.S.N = Fawn Suseptible count (scaler value >= 0),
#' 
#' juv.f.S.N = Juvenile Female Suseptible count (scaler value >= 0),
#' 
#' juv.m.S.N = Juvenile Male Suseptible count (scaler value >= 0),
#' 
#' ad.f.S.N = Adult Female Suseptible count (scaler value >= 0),
#' 
#' ad.m.S.N = Adult Male Suseptible count (scaler value >= 0),

## Exposed
#' fawn.E.N = Fawn exposed count (scaler value >= 0),
#' 
#' juv.f.E.N = Juvenile Female exposed count (scaler value >= 0),
#' 
#' juv.m.E.N = Juvenile Male exposed count (scaler value >= 0),
#' 
#' ad.f.E.N = Adult Female exposed count (scaler value >= 0),
#' 
#' ad.m.E.N = Adult Male exposed count (scaler value >= 0),


## Infected
#' 
#' juv.f.I.N = Juvenile Female infected count (scaler value >= 0),
#' 
#' juv.m.I.N = Juvenile Male infected count (scaler value >= 0),
#' 
#' ad.f.I.N = Adult Female infected count (scaler value >= 0),
#' 
#' ad.m.I.N = Adult Male infected count (scaler value >= 0),
```

survival 
*question: do we want different survival rates for infected age/sex classes or flat survival rate x mortality of being infected?*
```{r}
#' fawn.an.sur = annual fawn survival (scaler value between 0 and 1),  
#' 
#' juv.f.an.sur = annual juvenile female survival (scaler value between 0 and 1),  
#' 
#' juv.m.an.sur = annual juvenile male survival (scaler value between 0 and 1),  
#' 
#' ad.an.f.sur = annual adult female survival (scaler value between 0 and 1),  
#' 
#' ad.an.m.sur = annual adult male survival (scaler value between 0 and 1),
```

reproduction
```{r}
### female only 
#' 
#' juv.repro = juvenile reproduction (scaler value >= 0),  
#' 
#' ad.repro = adult reproduction (scaler value >= 0),
```

Harvest
```{r}
#' hunt.mort.fawn = percentage of fawns hunted (scaler value between 0 and 1),  
#' 
#' hunt.mort.juv.f = percentage of juvenile females hunted (scaler value between 0 and 1),  
#' 
#' hunt.mort.juv.m = percentage of juvenile males hunted (scaler value between 0 and 1),  
#' 
#' hunt.mort.ad.f = percentage of adult females hunted (scaler value between 0 and 1),  
#' 
#' hunt.mort.ad.m = percentage of adult males hunted (scaler value between 0 and 1),
```

disease state transition 
e = beta * no. infected * no susceptible + E
i = probability of transitioning 
```{r}
#' e.fawn.rate = rate of fawns moving from susceptible to exposed (scaler value between 0 and 1),  
#' 
#' e.ja.rate = rate of juvenile and adults moving from susceptible to exposed (scaler value between 0 and 1),  
#' 
#' i.rate = rate of all age classes moving from susceptible to exposed (scaler value between 0 and 1), 
#' 
```

Other parameters
Environmental Load: E_{t-1} + no. infectious individuals * shedding rate - decay/loss of prions + additional prions added through other pathways (carcass disposal)
Hunter popultion
```{r}
#'  
#' env = % of the population that is infected by the environment per month (scaler value between 0 and 1)
#' 
#' shedrate = the rate at which individuals infected with CWD release prions over 1 year
#' 
#' expdecayconstant = rate at which prions are lost from the environment over 1 year
#' 
#' ?beta.f = female transmission coefficient (scaler value greater than 0),  
#' 
#' ?beta.m = male transmission coefficient (scaler value greater than 0),  

```



The following conducts one run (timestep) of the population model 
Currently trying to fit and check with just susceptible category 
```{r}
params <- list(
  fawn.S.N = 100, juv.f.S.N = 50, juv.m.S.N = 50, ad.f.S.N = 80, ad.m.S.N = 20,
  fawn.E.N = 0, juv.f.E.N = 0, juv.m.E.N = 0, ad.f.E.N = 0, ad.m.E.N = 0,
  juv.f.I.N = 0, juv.m.I.N = 0, ad.f.I.N = 0, ad.m.I.N = 0,
  
  fawn.an.sur = 0.7, juv.f.an.sur = 0.9, juv.m.an.sur = .7, ad.an.f.sur = 0.95, ad.an.m.sur = 0.8, 
  
  juv.repro = 0.4, ad.repro = .9,
  
  hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.2, hunt.mort.ad.f = 0.15, hunt.mort.ad.m = 0.35, 
  
  e.fawn.rate = 0.0, e.ja.rate = 0.0, i.fawn.rate = 0.0, i.ja.rate = 0.0,
  
  env = 0, shedrate = .5, expdecayconstant = .55
  )


cwd_stoch_model <- function(params) {

  # check if static parameters exist.    
  if(exists("fawn.an.sur")==FALSE){
    message("fawn survival is missing, using default value")
    fawn.an.sur <- 0.6
  }
  
  if(exists("juv.f.an.sur")==FALSE){
    message("juvenile survival is missing, using default value")
    juv.f.an.sur <- 0.8
  } 
  
  
  ### Susceptible Category 
  # Fawns
  fawn.S.N_t1 <- (juv.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      (ad.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) +
    (juv.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      ( ad.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) +
    (juv.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      ( ad.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) )
 
   # Juveniles 
  juv.f.S.N_t1 <- .5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - e.fawn.rate)
  
  juv.m.S.N_t1 <- .5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - e.fawn.rate)
  
  # Adults 
  ad.f.S.N_t1 <- (ad.f.S.N * (1- hunt.mort.ad.f) * ad.an.f.sur * (1-e.ja.rate)) + 
    (juv.f.S.N * (1 - hunt.mort.juv.f) * juv.f.an.sur * (1-e.ja.rate))
  
  ad.m.S.N_t1 <- (ad.m.S.N * (1- hunt.mort.ad.m) * (1-e.ja.rate)) + 
    (juv.m.S.N * (1 - hunt.mort.juv.m) * juv.m.an.sur * (1-e.ja.rate))
  
  ### Exposed Category 
  # Fawns
  fawn.E.N_t1 <- (juv.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      (ad.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) +
    (juv.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      ( ad.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) +
    (juv.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      ( ad.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate )
  
  # Juveniles 
  juv.f.E.N_t1 <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * e.fawn.rate) + 
    (.5 * fawn.E.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - i.fawn.rate))
  
  juv.m.E.N_t1 <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * e.fawn.rate) + 
    (.5 * fawn.E.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - i.fawn.rate))
  
  # Adults 
  ad.f.E.N_t1 <- (ad.f.S.N * (1- hunt.mort.ad.f) * ad.an.f.sur * e.ja.rate) + 
    (ad.f.E.N * (1 - hunt.mort.ad.f) * ad.an.f.sur * (1 - i.ja.rate))
  
  ad.m.E.N_t1 <- (ad.m.S.N * (1- hunt.mort.ad.m) * ad.an.m.sur * e.ja.rate) + 
    (ad.m.E.N * (1 - hunt.mort.ad.m) * ad.an.m.sur * (1 - i.ja.rate))
  
  
  ### Infected Category 
  
  # Juveniles 
  juv.f.I.N_t1 <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * i.ja.rate) 
  
  juv.m.I.N_t1 <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * i.ja.rate)
  
  # Adults 
  ad.f.I.N_t1 <- (ad.f.E.N * (1- hunt.mort.ad.f) * ad.an.f.sur * i.ja.rate) + 
      (juv.f.E.N * (1 - hunt.mort.juv.f) * juv.f.an.sur * i.ja.rate) + 
    (ad.f.I.N * (1- hunt.mort.ad.f) * ad.an.f.sur) + 
      (juv.f.I.N * (1 - hunt.mort.juv.f) * juv.f.an.sur) 
  
  ad.m.I.N_t1 <- (ad.m.E.N * (1- hunt.mort.ad.m) * ad.an.m.sur * i.ja.rate) + 
      (juv.m.E.N * (1 - hunt.mort.juv.m) * juv.m.an.sur * i.ja.rate) + 
    (ad.m.I.N * (1- hunt.mort.ad.m) * ad.an.m.sur) + 
      (juv.m.I.N * (1 - hunt.mort.juv.m) * juv.m.an.sur) 
  
  
  ### Update the environmental load
  no.infect.indiv <- sum(juv.f.I.N_t1, juv.m.I.N_t1, ad.f.I.N_t1, ad.m.I.N_t1)
  env_t1 <- env + (no.infect.indiv * shedrate) - (expdecayconstant * env)
  
  ### Update e
  # This needs work!!!
  no.susceptible.indiv <- sum(juv.f.S.N_t1, juv.m.S.N_t1, ad.f.S.N_t1, ad.m.S.N_t1)
  # beta?? 
  # e = beta * no.infect.indiv * no.susceptible.indiv + env
  
    # group age/sex/disease stage population for t + 1 into one output 
  counts <- list(
      fawn.S.N_t1 = fawn.S.N_t1, juv.f.S.N_t1 = juv.f.S.N_t1, juv.m.S.N_t1 = juv.m.S.N_t1, ad.f.S.N_t1 = ad.f.S.N_t1, ad.m.S.N_t1 = ad.m.S.N_t1,
  fawn.E.N_t1 = fawn.E.N_t1, juv.f.E.N_t1 = juv.f.E.N_t1, juv.m.E.N_t1 = juv.m.E.N_t1, ad.f.E.N_t1 = ad.f.E.N_t1, ad.m.E.N_t1 = ad.m.E.N_t1,
   juv.f.I.N_t1 = juv.f.I.N_t1, juv.m.I.N_t1 = juv.m.I.N_t1, ad.f.I.N_t1 = ad.f.I.N_t1, ad.m.I.N_t1 = ad.m.I.N_t1)
  

  output <- counts #list(counts = counts.long)
  
  return(output)
}
  
```

```{r}
umm <- cwd_stoch_model(params)
```


Run for more than one time step 
```{r}
params <- list(
  fawn.S.N = 100, juv.f.S.N = 50, juv.m.S.N = 50, ad.f.S.N = 80, ad.m.S.N = 20,
  fawn.E.N = 0, juv.f.E.N = 0, juv.m.E.N = 0, ad.f.E.N = 0, ad.m.E.N = 0,
  juv.f.I.N = 0, juv.m.I.N = 0, ad.f.I.N = 0, ad.m.I.N = 0,
  
  fawn.an.sur = 0.7, juv.f.an.sur = 0.9, juv.m.an.sur = .7, ad.an.f.sur = 0.95, ad.an.m.sur = 0.8, 
  
  juv.repro = 0.4, ad.repro = .9,
  
  hunt.mort.fawn = 0.01, hunt.mort.juv.f = 0.1, hunt.mort.juv.m = 0.2, hunt.mort.ad.f = 0.15, hunt.mort.ad.m = 0.35, 
  
  e.fawn.rate = 0.0, e.ja.rate = 0.0, i.fawn.rate = 0.0, i.ja.rate = 0.0,
  
  env = 0, shedrate = .5, expdecayconstant = .55,
  
  nyears = 50
  )


cwd_stoch_model <- function(params) {

  # check if static parameters exist.    
  if(exists("fawn.an.sur")==FALSE){
    message("fawn survival is missing, using default value")
    fawn.an.sur <- 0.6
  }
  
  if(exists("juv.f.an.sur")==FALSE){
    message("juvenile survival is missing, using default value")
    juv.f.an.sur <- 0.8
  } 
  
  
  ### Create list to hold output for each year
  popout <- matrix(0, nrow = 14, ncol = nyears)
  dimnames(popout) <- list(c('fawn.S.N', 'juv.f.S.N', "juv.m.S.N", "ad.f.S.N", "ad.m.S.N", "fawn.E.N", "juv.f.E.N", "juv.m.E.N", "ad.f.E.N", "ad.m.E.N", "juv.f.I.N", "juv.m.I.N", "ad.f.I.N", "ad.m.I.N"), as.character(seq(1:nyears)))
  
  # for hunted
  hunted <- popout
  
  ### Populate with starting values
    counts <- list(
      fawn.S.N = fawn.S.N, juv.f.S.N = juv.f.S.N, juv.m.S.N = juv.m.S.N, ad.f.S.N = ad.f.S.N, ad.m.S.N = ad.m.S.N,
  fawn.E.N = fawn.E.N, juv.f.E.N = juv.f.E.N, juv.m.E.N = juv.m.E.N, ad.f.E.N = ad.f.E.N, ad.m.E.N = ad.m.E.N,
   juv.f.I.N = juv.f.I.N, juv.m.I.N = juv.m.I.N, ad.f.I.N = ad.f.I.N, ad.m.I.N = ad.m.I.N)

  popout[,1] <- unlist(counts)
  
  for(t in 2:nyears){
  
  ### Susceptible Category 
  # Fawns
  fawn.S.N <- (juv.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      (ad.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) +
    (juv.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      ( ad.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) +
    (juv.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) ) + 
      ( ad.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * (1-e.fawn.rate) )
 
   # Juveniles 
  juv.f.S.N <- .5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - e.fawn.rate)
  
  juv.m.S.N <- .5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - e.fawn.rate)
  
  # Adults 
  ad.f.S.N <- (ad.f.S.N * (1- hunt.mort.ad.f) * ad.an.f.sur * (1-e.ja.rate)) + 
    (juv.f.S.N * (1 - hunt.mort.juv.f) * juv.f.an.sur * (1-e.ja.rate))
  
  ad.m.S.N <- (ad.m.S.N * (1- hunt.mort.ad.m) * (1-e.ja.rate)) + 
    (juv.m.S.N * (1 - hunt.mort.juv.m) * juv.m.an.sur * (1-e.ja.rate))
  
  ### Exposed Category 
  # Fawns
  fawn.E.N <- (juv.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      (ad.f.S.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) +
    (juv.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      ( ad.f.E.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) +
    (juv.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate ) + 
      ( ad.f.I.N * (1- hunt.mort.juv.f) * juv.repro * juv.f.an.sur * e.fawn.rate )
  
  # Juveniles 
  juv.f.E.N <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * e.fawn.rate) + 
    (.5 * fawn.E.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - i.fawn.rate))
  
  juv.m.E.N <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * e.fawn.rate) + 
    (.5 * fawn.E.N * (1 - hunt.mort.fawn) * fawn.an.sur * (1 - i.fawn.rate))
  
  # Adults 
  ad.f.E.N <- (ad.f.S.N * (1- hunt.mort.ad.f) * ad.an.f.sur * e.ja.rate) + 
    (ad.f.E.N * (1 - hunt.mort.ad.f) * ad.an.f.sur * (1 - i.ja.rate))
  
  ad.m.E.N <- (ad.m.S.N * (1- hunt.mort.ad.m) * ad.an.m.sur * e.ja.rate) + 
    (ad.m.E.N * (1 - hunt.mort.ad.m) * ad.an.m.sur * (1 - i.ja.rate))
  
  
  ### Infected Category 
  
  # Juveniles 
  juv.f.I.N <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * i.ja.rate) 
  
  juv.m.I.N <- (.5 * fawn.S.N * (1 - hunt.mort.fawn) * fawn.an.sur * i.ja.rate)
  
  # Adults 
  ad.f.I.N <- (ad.f.E.N * (1- hunt.mort.ad.f) * ad.an.f.sur * i.ja.rate) + 
      (juv.f.E.N * (1 - hunt.mort.juv.f) * juv.f.an.sur * i.ja.rate) + 
    (ad.f.I.N * (1- hunt.mort.ad.f) * ad.an.f.sur) + 
      (juv.f.I.N * (1 - hunt.mort.juv.f) * juv.f.an.sur) 
  
  ad.m.I.N <- (ad.m.E.N * (1- hunt.mort.ad.m) * ad.an.m.sur * i.ja.rate) + 
      (juv.m.E.N * (1 - hunt.mort.juv.m) * juv.m.an.sur * i.ja.rate) + 
    (ad.m.I.N * (1- hunt.mort.ad.m) * ad.an.m.sur) + 
      (juv.m.I.N * (1 - hunt.mort.juv.m) * juv.m.an.sur) 
  
  
  ### Update the environmental load
  no.infect.indiv <- sum(juv.f.I.N, juv.m.I.N, ad.f.I.N, ad.m.I.N)
  env <- env + (no.infect.indiv * shedrate) - (expdecayconstant * env)
  
  ### Update e
  # This needs work!!! [after fitted to susceptible data..]
  no.susceptible.indiv <- sum(juv.f.S.N, juv.m.S.N, ad.f.S.N, ad.m.S.N)
  # beta?? 
  # e = beta * no.infect.indiv * no.susceptible.indiv + env
  
    # group age/sex/disease stage population for t + 1 into one output 
  counts <- list(
      fawn.S.N = fawn.S.N, juv.f.S.N = juv.f.S.N, juv.m.S.N = juv.m.S.N, ad.f.S.N = ad.f.S.N, ad.m.S.N = ad.m.S.N,
  fawn.E.N = fawn.E.N, juv.f.E.N = juv.f.E.N, juv.m.E.N = juv.m.E.N, ad.f.E.N = ad.f.E.N, ad.m.E.N = ad.m.E.N,
   juv.f.I.N = juv.f.I.N, juv.m.I.N = juv.m.I.N, ad.f.I.N = ad.f.I.N, ad.m.I.N = ad.m.I.N)

  popout[,t] <- unlist(counts)
  
  ## Need count of number of dead/removed individuals 
  
  hunted_indiv <- list(
      fawn.S.N = fawn.S.N * hunt.mort.fawn, juv.f.S.N = juv.f.S.N * hunt.mort.juv.f, juv.m.S.N = juv.m.S.N * hunt.mort.juv.m, ad.f.S.N = ad.f.S.N * hunt.mort.ad.f, ad.m.S.N = ad.m.S.N * hunt.mort.ad.m,
  fawn.E.N = fawn.E.N * hunt.mort.fawn, juv.f.E.N = juv.f.E.N * hunt.mort.juv.f, juv.m.E.N = juv.m.E.N * hunt.mort.juv.m, ad.f.E.N = ad.f.E.N * hunt.mort.ad.f, ad.m.E.N = ad.m.E.N * hunt.mort.ad.m,
   juv.f.I.N = juv.f.I.N * hunt.mort.juv.f, juv.m.I.N = juv.m.I.N * hunt.mort.juv.m, ad.f.I.N = ad.f.I.N * hunt.mort.ad.f, ad.m.I.N = ad.m.I.N * hunt.mort.ad.m)

  hunted[,t] <- unlist(hunted_indiv)
      
  } ## Close timeloop   

  output <- list(counts = popout, removed = hunted)
  
  return(output)
}
  
```


```{r}
popfit <- cwd_stoch_model(params)

counts_overtime <- popfit$counts

harvest_overtime <- popfit$removed
```

notes, these are fractional amounts. need to switch to whole numbers?








Set up a wrapper to run multiple times.. 
The following was taken from Paul Cross popn model
```{r}
popn_wrapper <- function(params, nsims) {
  
  if(missing(nsims) == T) warning('nsims not provided')
  if(missing(params) == T) warning('params not provided')
  
  #pre-allocate the output vectors
  counts.sims <- vector("list", nsims)
#  deaths.sims <- vector("list", nsims) # not using individual bins yet
  
  for(i in 1:nsims){
    outa <- cwd_stoch_model(params)
    counts.sims[[i]] <- outa
  }
}
```


```{r}
fitcheck <- popn_wrapper(params, nsims = 50)
```

```{r}
fitcheck
```






